---
title: "Gresham Lab Flow Core Guide"
author: '`r Sys.info()[7]`'
date: '`r Sys.Date()`'
output:
  html_document:
    fig_caption: yes
    keep_md: yes
    number_sections: yes
    toc: yes
---

Write a detailed description of your experiment here.  If you still see this text it means that you have not described the experiment and whatever follows is meaningless.

Be sure to include a relevant title

Delete text containing points 1-3 

This code is designed for use with the Accuri flow cytometer, which is equiped with the following lasers and filters

* Blue laser (488 nm)
  + FL1 filter = 514/20nm   GFP
  + FL3 filter = 575/25nm   YFP

* Yellow/green laser (552 nm)
  + FL2 filter = 610/20nm   mCherry, dtomato
  + FL4 filter = 586/15nm   DsRed

It is also designed for use with the CGSB Aria, which has the following lasers and printers

In order to run this code you need to predefine your gates using the gating.R script

This script generates a summary of results followed by quality control plots


#Step 1: Load relevant libraries 
```{r Libraries, eval=TRUE}
# This is a function that just makes sure you have a package, or installs it for you without prompting

requireInstall <- function(packageName,isBioconductor=F) {
  if ( !try(require(packageName,character.only=T)) ) {
    print(paste0("You don't have ",packageName," accessible, ",
      "I'm gonna install it"))
    if (isBioconductor) {
      source("http://bioconductor.org/biocLite.R")                        
      biocLite(packageName)                                                 
    } else {
      install.packages("packageName", repos = "http://cran.us.r-project.org")
    }
  }
  return(1)
}

#Load libraries
requireInstall("flowCore",isBioconductor=T)
requireInstall("flowViz",isBioconductor=T)
requireInstall("flowStats")
requireInstall("Hmisc")
requireInstall("reshape2")
requireInstall("ggplot2")
requireInstall("flowWorkspace")
requireInstall("ggcyto", isBioconductor=T)
requireInstall("gridExtra")


```

#Step 2: Read in .fcs files, an Rdata file containing the gates sample sheet(s) that contains four columns with 
* column1 = Well
* column2 = Strain
* column3 = Staining
* column4 = Media
* column5 = Userdefined

```{r}
#Read in all data for analysis. Data should be in individual directories that contain .fcs files and a corresponding sample sheet with a generic format. FCS file names should be unaltered e.g AO1.fcs, A02.fcs, ...H12.fcs 
#An abitrary number of directories can be used named dir1, dir2, dir3...with a corresponding flowData.1, flowData.2, flowData.3...and sample.sheet.1, sample.sheet.2, sample.sheet.3...

#load the Rdata file containing the gates
load("gates.Rdata") 

#Define how many directories that will be analyzed
num <- 2

#Define the directory, or directories, containing your .fcs files using absolute path names 
dir1 <- "/Users/David/Google Drive/Gresham Lab_David/flow/flow cytometry"
dir2 <- "/Users/David/Google Drive/Gresham Lab_David/flow/flow cytometry"

#Read in all the fcs files in the directory, with alter.names changing "-" to "."  
flowData.1 <- read.flowSet(path = dir1, pattern=".fcs", alter.names=TRUE)
flowData.2 <- read.flowSet(path = dir2, pattern=".fcs", alter.names=TRUE)

#Read in the sample sheet that should be in each directory that contains the .fcs files.  
sample.sheet.1 <- read.delim(paste(dir1, "SampleSheet.txt", sep="/"))
sample.sheet.2 <- read.delim(paste(dir1, "SampleSheet2.txt", sep="/"))

#Change names of samples to those specified in the sample sheets
sampleNames(flowData.1) <- paste(sample.sheet.1[,1], sample.sheet.1[,2], sample.sheet.1[,3], sample.sheet.1[,4], sample.sheet.1[,5], sample.sheet.1[,6], sep=" ")
sampleNames(flowData.2) <- paste(sample.sheet.2[,1], sample.sheet.2[,2], sample.sheet.2[,3], sample.sheet.2[,4], sample.sheet.2[,5], sample.sheet.2[,6], sep=" ")
```


```{r}
#Check how many cells were counted in each fcs file
fsApply(flowData.1, each_col, length)[1:6]
fsApply(flowData.2, each_col, length)[1:6]

total.1 <- fsApply(flowData.1, each_col, length)[1:6]  #total counts per sample
total.2 <- fsApply(flowData.1, each_col, length)[1:6] #total counts per sample

#Print the medians of data values for each measurement
fsApply(flowData.1, each_col, median)
fsApply(flowData.2, each_col, median)

#combine all flowSets into a single flowset
flowData <- rbind2(flowData.1, flowData.2)
total <- fsApply(flowData, each_col, length)[1:12] #total number of measurements per sample
fsApply(flowData, each_col, median)
samples.num <- length(flowData)

```

#Step 3: apply filters to data and generate plots showing the effect on filtering
```{r}
##Subset the data by applying sequential gates##

#apply doublet gate
flowData.singlets <- Subset(flowData, pg.singlets) 
fsApply(flowData.singlets, each_col, length)[1:samples.num]
singlets <- fsApply(flowData.singlets, each_col, length)[1:samples.num]
barplot(singlets/total, ylim=c(0,1), ylab = "Proportion singlet cells", las=2, cex.names = 0.5, names.arg=sampleNames(flowData))

#apply debris gate
filteredData <- Subset(flowData.singlets, pg.nondebris) 
fsApply(filteredData, each_col, length)[1:samples.num]
non.debris <- fsApply(filteredData, each_col, length)[1:samples.num]
barplot(non.debris/total, ylim=c(0,1), ylab = "Proportion singlet and nondebris cells", las=2, cex.names = 0.5, names.arg=sampleNames(flowData))

#########
#filteredData is the variable name for the data filtered of doublets and debris that are used for all subsequent analyses
##########

#this gate defines nongfp cells
gfp.neg <- Subset(filteredData, pg.nongfp) 
fsApply(gfp.neg, each_col, length)[1:samples.num]
non.gfp <- fsApply(gfp.neg, each_col, length)[1:samples.num]
barplot(non.gfp/non.debris, ylim=c(0,1), ylab = "Proportion cells with no GFP", las=2, cex.names = 0.5, names.arg=sampleNames(flowData))

#this gate defines gfp cells
gfp.pos <- Subset(filteredData, pg.gfp) 
fsApply(gfp.pos, each_col, length)[1:samples.num]
gfp.cells <- fsApply(gfp.pos, each_col, length)[1:samples.num]
barplot(gfp.cells/non.debris, ylim=c(0,1), ylab = "Proportion cells with GFP", las=2, cex.names = 0.5, names.arg=sampleNames(flowData))

#this gate defines high GFP cells
gfp.hi <- Subset(filteredData, pg.hi.gfp) 
fsApply(gfp.hi, each_col, length)[1:samples.num]
hi.gfp.cells <- fsApply(gfp.hi, each_col, length)[1:samples.num]
barplot(hi.gfp.cells/non.debris, ylim=c(0,1), ylab = "Proportion cells with high GFP", las=2, cex.names = 0.5, names.arg=sampleNames(flowData))
```

#Step 4: Data analysis

##diagnostic values can be defined for plotting purposes
```{r}
#define critical values that can superimposed on plots for easy visual comparison

gfp.bg <- 3.9  #a background value for GFP
gfp.wt <- 5.9 #a value for wildtype GFP expression
red.bg <- 3.03 #a background value for the red channel
red.wt <- 3.75 #a value for wildtype Red expression
haploid.fsc <- 6e5 #an empirical value for forward scatter for haploids
diploid.fsc <- 7e5 #an empirical value for forward scatter for diploids
gfp.norm <- 0.935 #an empricial value for gfp expression normalized by forward scatter
red.norm <- 0.57 #an empricial value for red expression normalized by forward scatter
gfp.red.norm <- 1.5 #an empricial value for gfp expression normalized by red channel

```

##Extract data from fcs files to generate statistics and boxplots
```{r}
#record summary statistics for each sample in a matrix named summary.stats 
summary.stats <- matrix(data = NA, nrow = length(filteredData), ncol = 18, dimnames = list(sampleNames(filteredData),c("FSC_median","FSC_mean", "FSC_sd","FL1_median", "FL1_mean","FL1_sd","normalizedGFP_median", "normalizedGFP_mean", "normalizedGFP_sd","FL2_median","FL2_mean","FL2_sd","normalizedRed_median","normalizedRed_mean", "normalizedRed_sd","GFPnormalizedByRed_median", "GFPnormalizedByRed_mean","GFPnormalizedByRed_sd")))

#use the sample containing the minimum number of points after filtering for doublets and debris to define the number of data points retained for all samples
sample.size <- min(fsApply(filteredData, each_col, length))  

print(sample.size)

comparison.FSC <- matrix(data = NA, nrow = sample.size, ncol = length(filteredData), byrow = FALSE,dimnames = NULL)
comparison.FL1 <- matrix(data = NA, nrow = sample.size, ncol = length(filteredData), byrow = FALSE,dimnames = NULL)
comparison.FL2 <- matrix(data = NA, nrow = sample.size, ncol = length(filteredData), byrow = FALSE,dimnames = NULL)
comparison.FL1NormFsc <- matrix(data = NA, nrow = sample.size, ncol = length(filteredData), byrow = FALSE,dimnames = NULL)
comparison.FL2NormFsc <- matrix(data = NA, nrow = sample.size, ncol = length(filteredData), byrow = FALSE,dimnames = NULL)
comparison.FL1NormFL2 <- matrix(data = NA, nrow = sample.size, ncol = length(filteredData), byrow = FALSE,dimnames = NULL)

#for each sample plot a histogram of the normalized data, raw FSC and raw GFP per row
par(mfrow=c(1,2), mar=c(5.1,2.1,2.1,2.1), oma=c(1.5,2,1,1))

#extract data from flowFrames to plot histograms of values and record summary statistics
for (i in 1:length(filteredData)){
 
  temp <- exprs(filteredData[[i]]) #exprs() extracts a matrix of the values from the flowframe
 

  ##########################################
  #record summary statistics for the sample#
  ##########################################
  
  #FSC
  summary.stats[i,1] <- median(temp[,1]) 
  summary.stats[i,2] <-mean(temp[,1])  
  summary.stats[i,3] <- sd(temp[,1])
  #FL1
  summary.stats[i,4] <- median(temp[,3])
  summary.stats[i,5] <-mean(temp[,3])  
  summary.stats[i,6] <- sd(temp[,3])
  #FL1 (GFP) divided by FSC
  summary.stats[i,7] <- median(temp[,3]/temp[,1])
  summary.stats[i,8] <-mean(temp[,3]/temp[,1])  
  summary.stats[i,9] <- sd(temp[,3]/temp[,1])
  #FL2
  summary.stats[i,10] <- median(temp[,4])
  summary.stats[i,11] <-mean(temp[,4])  
  summary.stats[i,12] <- sd(temp[,4])
  #FL2 (Red) divided by FSC
  summary.stats[i,13] <- median(temp[,4]/temp[,1])
  summary.stats[i,14] <-mean(temp[,4]/temp[,1])  
  summary.stats[i,15] <- sd(temp[,4]/temp[,1])
  #FL1 (GFP) divided by FL2 (Red)
  summary.stats[i,16] <- median(temp[,3]/temp[,4])
  summary.stats[i,17] <-mean(temp[,3]/temp[,4])  
  summary.stats[i,18] <- sd(temp[,3]/temp[,4])  
  
  ##############################################
  #plot histograms of the channels of interest##
  ##############################################

  ###############
  #Green channel#
  ###############
  
  #FL1 (GFP)
  hist(log10(temp[,3]), br=1000, xlab = "FL1", main = "FL1") 
  abline(v=gfp.bg, col="yellow", lty=2, lwd=2)
  abline(v=gfp.wt, col="green", lty=2, lwd=2) 
  legend("topleft",  legend=paste("median FL1 = ",round(median(temp[,3]), digits=4),sep=""))

  #GFP divided by FSC
  hist(temp[,3]/temp[,1], br=500, xlim=c(0,1.5), xlab = "FL1/FSC", main = "FL1/FSC") 
  abline(v=gfp.norm, col="green", lty=2, lwd=2 )
  legend("topleft",  legend=paste("median GFP / FSC=",round(median(temp[,3]/temp[,1]), digits=4),sep=""))
  
  mtext(sampleNames(filteredData[i]), outer = TRUE, cex = 1.0)
  
  ###############
  #Red channel#
  ###############
  #FL2 (Red)
  hist(log10(temp[,4]), br=500, xlab = "FL2", main = "FL2") 
  abline(v=red.bg, col="yellow", lty=2, lwd=2)
  abline(v=red.wt, col="red", lty=2, lwd=2) 
  legend("topleft",  legend=paste("median FL2=",round(median(temp[,4]), digits=4),sep=""))
 
  #FL2 divided by FSC
  hist(temp[,4]/temp[,1], br=500, xlim=c(0,1.5), xlab = "FL2/FSC", main = "FL2/FSC") 
  abline(v=red.norm, col="red", lty=2, lwd=2 )
  legend("topleft",  legend=paste("median FL2 / FSC=",round(median(temp[,4]/temp[,1]), digits=4),sep=""))

  mtext(sampleNames(filteredData[i]), outer = TRUE, cex = 1.0)
  
  ###############
  #Other#########
  ###############
  
  #FL1 divided by FL2
  hist(temp[,4]/temp[,3], br=500, xlim=c(0,1.5), xlab = "FL2/FL1", main = "FL1/FL2") 
  abline(v=gfp.red.norm, col="purple", lty=2, lwd=2)
  legend("topleft",  legend=paste("median FL1 / FL2=",round(median(temp[,4]/temp[,3]), digits=4),sep=""))

    #FSC
  hist(log10(temp[,1]), br=500, xlab = "FSC", main = "FSC", xlim=c(4,8)) 
  abline(v=haploid.fsc, col="blue", lty=2, lwd=2)
  abline(v=diploid.fsc, col="grey", lty=2, lwd=2)
  legend("topleft",  legend=paste("median FSC=",round(median(temp[,1]), digits=4),sep=""))
  
  mtext(sampleNames(filteredData[i]), outer = TRUE, cex = 1.0)

print("-------------------------------------------------------")
print("-----------------------------------")
print("----------------------")

  ############################################################
  #keep the data set for generating boxplots comparing values#
  ############################################################
  
  #Note that the amount of data kept for each sample is defined by the lowest count among all the samples.
  comparison.FSC[1:sample.size,i] <- temp[1:sample.size,1] #FSC
  comparison.FL1[1:sample.size,i] <- temp[1:sample.size,3] #FL1 (GFP)
  comparison.FL1NormFsc[1:sample.size,i] <- temp[1:sample.size,3]/temp[1:sample.size,1] #GFP/FSC
  comparison.FL2[1:sample.size,i] <- temp[1:sample.size,4] #FL2 
  comparison.FL2NormFsc[1:sample.size,i] <- temp[1:sample.size,4]/temp[1:sample.size,1] #FL2/FSC
  comparison.FL1NormFL2[1:sample.size,i] <- temp[1:sample.size,3]/temp[1:sample.size,4] #FL1/FL2
  
}

par(mfrow=c(1,1)) #change number of plots per row back to standard

```


##Overview of data distributions
```{r}
par(mar=c(8.1,4.1,4.1,2.1)) #create more space at lower margin
#boxplot(comparison.FSC, names=sampleNames(filterData), notch = TRUE, col = "gray", ylab="FSC", cex.axis=0.5,las=2, outline=F)
#j <- 3 #desired label: 1 = Well, 2 = strain, 3 = genotype, 4 = ploidy, 5 = media

boxplot(comparison.FSC, names=sampleNames(filteredData), notch = TRUE, col = "gray", ylab="FSC", cex.axis=0.5,las=2, outline=F)
abline(h=haploid.fsc, lty=2, col=2)
abline(h=diploid.fsc, lty=2, col=3)

boxplot(comparison.FL1, names=sampleNames(filteredData), notch = TRUE, col = "lightgreen", ylab="FL1", cex.axis=0.5,las=2, outline=F)
abline(h=gfp.bg ,lty=2, lwd=3, col="yellow")
abline(h=gfp.wt, lty = 2, lwd=3, col="green")

boxplot(comparison.FL1NormFsc, names=sampleNames(filteredData), notch = TRUE, col = "green", ylab="FL1/FSC", cex.axis=0.5,las=2, outline=F)
abline(h=gfp.norm, lty=2, lwd=3, col="blue")

boxplot(comparison.FL2, names=sampleNames(filteredData), notch = TRUE, col = "pink", ylab="FL2", cex.axis=0.5,las=2, outline=F)
abline(h=red.bg, lty=2, lwd=3, col="pink")
abline(h=red.wt, lty=2, lwd=3, col="red")

boxplot(comparison.FL2NormFsc, names=sampleNames(filteredData), notch = TRUE, col = "red", ylab="FL2/FSC", cex.axis=0.5,las=2, outline=F)
abline(h=red.norm, lty=2, lwd=3, col="red")

boxplot(comparison.FL1NormFL2, names=sampleNames(filteredData), notch = TRUE, col = "purple", ylab="FL1/FL2", cex.axis=0.5,las=2, outline=F)
abline(h=gfp.red.norm, lty=2, lwd=3, col="purple")

par(mar=c(5.1,4.1,4.1,2.1)) #reset margins to default

#generate a summary table containing all the recorded statistics
print(summary.stats)
summary.stats <- as.data.frame(summary.stats)

```


##Quantitation of relative FL1 signal
```{r}
baseline.FL1 <- summary.stats$FL1_median[1]

barplot(summary.stats$FL1_median/baseline.FL1, ylab="Relative expression", las=2, cex.names = 0.5, names.arg=sampleNames(filteredData))

```

##Quantitation of forward scatter
```{r}
baseline.FSC <- summary.stats$FSC_median[1]

barplot(summary.stats$FSC_median/baseline.FSC, ylab="Relative expression", las=2, cex.names = 0.5, names.arg=sampleNames(filteredData))

```

##Population composition
```{r}
pop.composition <- rbind(non.gfp/non.debris,gfp.cells/non.debris,hi.gfp.cells/non.debris)
barplot(pop.composition, ylab="Proportion of population", legend=c("No GFP", "Normal GFP", "High GFP"),las=2, cex.names = 0.5,names.arg=sampleNames(filteredData))

```

#Step 5: Quality control

##Gates
```{r}
###First flowset
#Singlets gate
xyplot(FSC.A~FSC.H, data=flowData.1, xlim=c(0,3e6), ylim=c(0,3e6), filter=pg.singlets,  smooth=F, xbin=1024, stat=T, pos=0.5, abs=T, main = "First flowset")

#Debris gate
xyplot(SSC.A ~ FSC.A, data=flowData.1, displayFilter=TRUE, xlim=c(0,3e5), ylim=c(0,3e6), filter=pg.nondebris, smooth=F, xbin=1024, stat=T, pos=0.5, abs=T,  main = "First flowset")

#Non-fluorescent population gate
xyplot(FL1.A~FSC.A,data=flowData.1, displayFilter=TRUE, xlim=c(0,5e6), ylim=c(0,5e4), filter=pg.nongfp, smooth=F, xbin=1024, stat=T, pos=0.5, abs=T,  main = "First flowset")

#Fluorescent population gate
xyplot(FL1.A~FSC.A,data=flowData.1, displayFilter=TRUE, xlim=c(0,5e6), ylim=c(0,5e4), filter=pg.gfp, smooth=F, xbin=1024, stat=T, pos=0.5, abs=T, main = "First flowset")

#High fluorescing gate
xyplot(FL1.A~FSC.A,data=flowData.1, xlim=c(0,5e6), ylim=c(0,5e4), filter=pg.hi.gfp, smooth=F, xbin=1024, stat=T, pos=0.5, abs=T,  main = "First flowset")

################
###Second flowset
#Singlets gate
xyplot(FSC.A~FSC.H, data=flowData.2, xlim=c(0,3e6), ylim=c(0,3e6), filter=pg.singlets,  smooth=F, xbin=1024, stat=T, pos=0.5, abs=T, main = "Second flowset")

#Debris gate
xyplot(SSC.A ~ FSC.A, data=flowData.2, displayFilter=TRUE, xlim=c(0,3e6), ylim=c(0,3e5), filter=pg.nondebris, smooth=F, xbin=1024, stat=T, pos=0.5, abs=T,  main = "Second flowset")

#Non-fluorescent population gate
xyplot(FL1.A~FSC.A,data=flowData.2, displayFilter=TRUE, xlim=c(0,5e6), ylim=c(0,5e4), filter=pg.nongfp, smooth=F, xbin=1024, stat=T, pos=0.5, abs=T,  main = "Second flowset")

#Fluorescent population gate
xyplot(FL1.A~FSC.A,data=flowData.2, displayFilter=TRUE, xlim=c(0,5e6), ylim=c(0,5e4), filter=pg.gfp, smooth=F, xbin=1024, stat=T, pos=0.5, abs=T, main = "Second flowset")

#High fluorescing gate
xyplot(FL1.A~FSC.A,data=flowData.2, xlim=c(0,5e6), ylim=c(0,5e4), filter=pg.hi.gfp, smooth=F, xbin=1024, stat=T, pos=0.5, abs=T,  main = "Second flowset")





#####Attempted as look below and is not working

for (i in 1:length(filteredData)){

#Singlets gate
xyplot(FSC.A~FSC.H, data=flowData[i], xlim=c(0,3e6), ylim=c(0,3e6), filter=pg.singlets,  smooth=F, xbin=1024, stat=T, pos=0.5, abs=T, main = sampleNames(flowData)[i])

#Debris gate
xyplot(SSC.A ~ FSC.A, data=flowData[i], displayFilter=TRUE, xlim=c(0,3e5), ylim=c(0,3e6), filter=pg.nondebris, smooth=F, xbin=1024, stat=T, pos=0.5, abs=T, main = sampleNames(flowData)[i])

#Non-fluorescent population gate
xyplot(FL1.A~FSC.A,data=flowData[i], displayFilter=TRUE, xlim=c(0,5e6), ylim=c(0,5e4), filter=pg.nongfp, smooth=F, xbin=1024, stat=T, pos=0.5, abs=T, main = sampleNames(flowData)[i])

#Fluorescent population gate
xyplot(FL1.A~FSC.A,data=flowData[i], displayFilter=TRUE, xlim=c(0,5e6), ylim=c(0,5e4), filter=pg.gfp, smooth=F, xbin=1024, stat=T, pos=0.5, abs=T, main = sampleNames(flowData)[i])

#High fluorescing gate
xyplot(FL1.A~FSC.A,data=flowData[i], xlim=c(0,5e6), ylim=c(0,5e4), filter=pg.hi.gfp, smooth=F, xbin=1024, stat=T, pos=0.5, abs=T, main = sampleNames(flowData)[i])


}
```


##Data transformation for visualization
```{r}
#In order to look at QC plots the data is transformed using the logicle transform, which is a log transform for high values that transitions to a linear transformation near zero values 

#This is simply for visualization purposes

lgcl <- logicleTransform(w = 0.5, t= 10000, m=4.5) #the parameters w,t, and m define the transformation parameters

#Dataset 1 tranformation applied to every channel except width and time
dataLGCLTransform <- transform(filteredData,'FSC.A' = lgcl(`FSC.A`), 'SSC.A' =lgcl(`SSC.A`), 'FL1.A' = lgcl(`FL1.A`), 'FL2.A' = lgcl(`FL2.A`), 'FL3.A' = lgcl(`FL3.A`), 'FL4.A' = lgcl(`FL4.A`),'FSC.H' = lgcl(`FSC.H`),'SSC.H' = lgcl(`SSC.H`),'FL1.H' = lgcl(`FL1.H`),'FL2.H' = lgcl(`FL2.H`),'FL3.H' = lgcl(`FL3.H`),'FL4.H' = lgcl(`FL4.H`)) 

```

##Effect of time
```{r}
#The effect of time on signal (of which there shouldn't be any)
i <- 1
xyplot(FL1.A ~ Time, data=dataLGCLTransform[i], smooth=F,  stat=T, pos=0.5, abs=T, xlim=c(150,250), main = sampleNames(filteredData)[i])
####Attempted as loop and will not work 
for (i in 1:length(filteredData)){
xyplot(FL1.A ~ Time, data=dataLGCLTransform[i], smooth=F,  stat=T, pos=0.5, abs=T, xlim=c(150,250), main = sampleNames(filteredData)[i])
}
```

##Plots of FL1 versus FSC
```{r}
xyplot(FL1.A ~ FSC.A, data=dataLGCLTransform[i], smooth=F,  stat=T, pos=0.5, abs=T, xlim=c(4,8), ylim=c(2,6), sampleNames(filteredData)[i])
####Attempted as loop and will not work 
for (i in 1:length(filteredData)){
xyplot(FL1.A ~ FSC.A, data=dataLGCLTransform[i], smooth=F,  stat=T, pos=0.5, abs=T, xlim=c(4,8), ylim=c(2,6), sampleNames(filteredData)[i])
}
```

##Plots of FSC versus SSC
```{r}
xyplot(SSC.A ~ FSC.A, data=dataLGCLTransform[i], smooth=F,  stat=T, pos=0.5, abs=T, xlim=c(4,8), ylim=c(4,8), sampleNames(filteredData)[i])
####Attempted as loop and will not work 
for (i in 1:length(filteredData)){
xyplot(SSC.A ~ FSC.A, data=dataLGCLTransform[i], smooth=F,  stat=T, pos=0.5, abs=T, xlim=c(4,8), ylim=c(4,8), sampleNames(filteredData)[i])
}
```





