---
title: "Gresham Lab Flow Core Guide"
author: '`r Sys.info()[7]`'
date: '`r Sys.Date()`'
output:
  html_document:
    fig_caption: yes
    keep_md: yes
    number_sections: yes
    toc: yes
---

#1) Write a detailed description of your experiment here.  If you still see this text it means that you have not described the experiment and whatever follows is meaningless.

#2) Be sure to include a relevant title

#3) Delete text containing points 1-3 

###This code is designed for use with the Accuri flow cytometer, which is equiped with the following lasers and filters

* Blue laser (488 nm)
  + FL1 filter = 514/20nm   GFP
  + FL3 filter = 575/25nm   YFP

* Yellow/green laser (552 nm)
  + FL2 filter = 610/20nm   mCherry, dtomato
  + FL4 filter = 586/15nm   DsRed

###It is also designed for use with the CGSB Aria, which has the following lasers and printers

###In order to run this code you need to predefine your gates using the gating.R script

###This script generates a summary of results followed by quality control plots

###Step 1: Load relevant libraries 

```{r, eval=FALSE}
# This is a function that just makes sure you have a package, or installs it for you without prompting

requireInstall <- function(packageName,isBioconductor=F) {
  if ( !try(require(packageName,character.only=T)) ) {
    print(paste0("You don't have ",packageName," accessible, ",
      "I'm gonna install it"))
    if (isBioconductor) {
      source("http://bioconductor.org/biocLite.R")                        
      biocLite(packageName)                                                 
    } else {
      install.packages("packageName")
    }
  }
  return(1)
}

#Load libraries
requireInstall("flowCore",isBioconductor=T)
requireInstall("flowViz",isBioconductor=T)
#requireInstall("flowStats")
#requireInstall("Hmisc")
requireInstall("reshape2")
requireInstall("ggplot2")
#requireInstall("flowWorkspace")
#requireInstall("ggcyto", isBioconductor=T)
#requireInstall("gridExtra")

```

###Step 2: Read in .fcs files, an Rdata file containing the gates sample sheet(s) that contains four columns with 
* column1 = Well
* column2 = Strain
* column3 = Staining
* column4 = Media
* column5 = Userdefined

```{r}
#Read in all data for analysis. Data should be in individual directories that contain .fcs files and a corresponding sample sheet with a generic format. FCS file names should be unaltered e.g AO1.fcs, A02.fcs, ...H12.fcs 
#An abitrary number of directories can be used named dir1, dir2, dir3...with a corresponding flowData.1, flowData.2, flowData.3...and sample.sheet.1, sample.sheet.2, sample.sheet.3...

#load the Rdata file containing the gates
load("gates.Rdata") 

#Define how many directories that will be analyzed
num <- 1

#Define the directory, or directories, containing your .fcs files using absolute path names 
dir1 <- "/Users/David/Google Drive/Gresham Lab_David/flow/flow cytometry"
#dir2 <- "/Users/David/Google Drive/Gresham Lab_David/GreshamLab Flow Cytometry 2016/2015_12_02"

#Read in all the fcs files in the directory, with alter.names changing "-" to "."  
flowData.1 <- read.flowSet(path = dir1, pattern=".fcs", alter.names=TRUE)
#flowData.2 <- read.flowSet(path = dir2, pattern=".fcs", alter.names=TRUE)

#Read in the sample sheet that should be in each directory that contains the .fcs files.  
sample.sheet.1 <- read.csv(paste(dir1, "SampleSheet.csv", sep="/"))
#sample.sheet.2 <- read.csv(paste(dir2, "SampleSheet.csv", sep="/"))

```


```{r}
#Check how many cells were counted in each fcs file
fsApply(flowData.1, each_col, length)
#fsApply(flowData.2, each_col, length)

#Print the medians of data
fsApply(flowData.1, each_col, median)
#fsApply(flowData.2, each_col, median)
```

###Step 4: Transform data and create gates to filter out debris

Apply logicle tranformation of data
```{r}
#Perform the logicle transform, which is a log transform for high values that transitions to a linear transformation near zero values
lgcl <- logicleTransform(w = 0.5, t= 10000, m=4.5) #the parameters w,t, and m define the transformation parameters

#Dataset 1 tranformation applied to every channel except width and time
dataLGCLTransform.1 <- transform(flowData.1,'FSC.A' = lgcl(`FSC.A`), 'SSC.A' =lgcl(`SSC.A`), 'FL1.A' = lgcl(`FL1.A`), 'FL2.A' = lgcl(`FL2.A`), 'FL3.A' = lgcl(`FL3.A`), 'FL4.A' = lgcl(`FL4.A`),'FSC.H' = lgcl(`FSC.H`),'SSC.H' = lgcl(`SSC.H`),'FL1.H' = lgcl(`FL1.H`),'FL2.H' = lgcl(`FL2.H`),'FL3.H' = lgcl(`FL3.H`),'FL4.H' = lgcl(`FL4.H`)) 

#Dataset 2 tranformation applied to every channel
dataLGCLTransform.2 <- transform(flowData.2,'FSC.A' = lgcl(`FSC.A`), 'SSC.A' =lgcl(`SSC.A`), 'FL1.A' = lgcl(`FL1.A`), 'FL2.A' = lgcl(`FL2.A`), 'FL3.A' = lgcl(`FL3.A`), 'FL4.A' = lgcl(`FL4.A`),'FSC.H' = lgcl(`FSC.H`),'SSC.H' = lgcl(`SSC.H`),'FL1.H' = lgcl(`FL1.H`),'FL2.H' = lgcl(`FL2.H`),'FL3.H' = lgcl(`FL3.H`),'FL4.H' = lgcl(`FL4.H`)) 


##Apply a rectangle gate based on FSC and SSC to remove values that we have determined are typically debris for haploid cells.  This should be adjusted if the cell type is different
rectGate <- rectangleGate("FSC.A"= c(5.8,7),"SSC.A" = c(4.8,6.7))

xyplot(FSC.A ~ SSC.A, data=dataLGCLTransform.1, ylim=c(3,8),xlim=c(3,8), displayFilter=TRUE, filter=rectGate, smooth=F, xbin=128, stat=T, pos=0.5, abs=T)

#Subset the filtered data
filterData.1 <- Subset(dataLGCLTransform.1, rectGate) #this gets the filtered data in a new flowSet
filterData.2 <- Subset(dataLGCLTransform.2, rectGate) #this gets the filtered data in a new flowSet

##Apply a manually drawing gate based on FSC.A and FSC.H to remove values that are doublets for haploid cells.  



#To look at the effect of time on signal (of which there shouldn't be any)
xyplot(FL1.A ~ Time, data=dataLGCLTransform.1[[1]], smooth=F,  stat=T, pos=0.5, abs=T, xlim=c(0,500))
xyplot(FL1.A ~ Time, data=dataLGCLTransform.1[[2]], smooth=F,  stat=T, pos=0.5, abs=T, xlim=c(0,500))
xyplot(FL1.A ~ Time, data=dataLGCLTransform.1[[3]], smooth=F,  stat=T, pos=0.5, abs=T, xlim=c(0,500))
xyplot(FL1.A ~ Time, data=dataLGCLTransform.1[[4]], smooth=F,  stat=T, pos=0.5, abs=T, xlim=c(0,500))
xyplot(FL1.A ~ Time, data=dataLGCLTransform.1[[5]], smooth=F,  stat=T, pos=0.5, abs=T, xlim=c(0,500))
xyplot(FL1.A ~ Time, data=dataLGCLTransform.1[[6]], smooth=F,  stat=T, pos=0.5, abs=T, xlim=c(0,500))
xyplot(FL1.A ~ Time, data=dataLGCLTransform.1[[7]], smooth=F,  stat=T, pos=0.5, abs=T, xlim=c(0,500))
xyplot(FL1.A ~ Time, data=dataLGCLTransform.1[[8]], smooth=F,  stat=T, pos=0.5, abs=T, xlim=c(0,500))
xyplot(FL1.A ~ Time, data=dataLGCLTransform.1[[9]], smooth=F,  stat=T, pos=0.5, abs=T, xlim=c(0,500))
xyplot(FL1.A ~ Time, data=dataLGCLTransform.1[[10]], smooth=F,  stat=T, pos=0.5, abs=T, xlim=c(0,500))

xyplot(FSC.A~FSC.H, data=filterData, xlim=c(5,7.5),ylim=c(5,7.5),
       smooth=F, filter=pg, outline=T, displayFilter=TRUE,
       stat=T, pos=0.5, abs=T)
singletsData <- Subset(filterData, pg) 



##Apply a rectangle gate based on FSC and SSC to remove values that we have determined are typically debris for haploid cells.  This should be adjusted if the cell type is different
rectGate <- rectangleGate("FSC.A"= c(5.6,7.6),"SSC.A" = c(4.6,6.8))

#Subset the filtered data to remove outliers defined by FFC and SSC 
filterData <- Subset(dataLGCLTransform, rectGate) 

#Check medians of filtered data
fsApply(filterData, each_col, median)
```

Plot the rectangle gate used for filtering and determine the proportion of cells used for subsequent analysis
```{r}
##Plot the rectangle gate used to filter on the basis of SSC and FSC to ensure that most cells are retained in analysis.
xyplot(FSC.A ~ SSC.A, data=dataLGCLTransform, ylim=c(3,8),xlim=c(3,8), displayFilter=TRUE, filter=rectGate, smooth=F, xbin=128, stat=T, pos=0.5, abs=T)
```

Plot an overview of the data
```{r}
##Plot FFS versus SSC
xyplot(SSC.A ~ FSC.A, data=filterData, ylim=c(3,8),xlim=c(3,8), smooth=F, xbin=128)

##Plot FL1(GFP) versus FSC 
xyplot(FL1.A ~ FSC.A, data=filterData, ylim=c(2,7),xlim=c(5,8), smooth=F, xbin=128)

##Plot FL2(mCherry) versus FSC 
xyplot(FL2.A ~ FSC.A, data=filterData, ylim=c(2,7),xlim=c(5,8), smooth=F, xbin=128)

##Plot FL1 (GFP) versus FL2 (Red)
xyplot(FL1.A ~ FL2.A, data=filterData, ylim=c(1,8),xlim=c(0,6), smooth=F, xbin=128)

```


###Step 5: Quantify fluorescence for each sample and plot a histogram

diagnostic values can be defined for plotting purposes
```{r}
#define critical values that can superimposed on plots for easy visual comparison

gfp.bg <- 3.9  #a background value for GFP
gfp.wt <- 5.9 #a value for wildtype GFP expression
red.bg <- 3.03 #a background value for the red channel
red.wt <- 3.75 #a value for wildtype Red expression
haploid.fsc <- 6.43 #an empirical value for forward scatter for haploids
diploid.fsc <- 6.54 #an empirical value for forward scatter for diploids
gfp.norm <- 0.935 #an empricial value for gfp expression normalized by forward scatter
red.norm <- 0.57 #an empricial value for red expression normalized by forward scatter
gfp.red.norm <- 1.5 #an empricial value for gfp expression normalized by red channel

```


```{r}
#record summary statistics in a matrix 
summary.stats <- matrix(data = NA, nrow = length(filterData), ncol = 18, dimnames = list(sampleNames(filterData),c("FSC_median","FSC_mean", "FSC_sd","FL1_median", "FL1_mean","FL1_sd","normalizedGFP_median", "normalizedGFP_mean", "normalizedGFP_sd","FL2_median","FL2_mean","FL2_sd","normalizedRed_median","normalizedRed_mean", "normalizedRed_sd","GFPnormalizedByRed_median", "GFPnormalizedByRed_mean","GFPnormalizedByRed_sd")))

#retain ratio of GFP(i.e. FL1.A) to FSC.A for generating boxplot as well as FSC and FL1A 
total <- min(fsApply(filterData, each_col, length)) #use the sample containing the minimum number of points after size-based filtering to define the size of the matrix 

print(total)

comparison.FSC <- matrix(data = NA, nrow = total, ncol = length(filterData), byrow = FALSE,dimnames = NULL)
comparison.FL1 <- matrix(data = NA, nrow = total, ncol = length(filterData), byrow = FALSE,dimnames = NULL)
comparison.FL2 <- matrix(data = NA, nrow = total, ncol = length(filterData), byrow = FALSE,dimnames = NULL)
comparison.FL1NormFsc <- matrix(data = NA, nrow = total, ncol = length(filterData), byrow = FALSE,dimnames = NULL)
comparison.FL2NormFsc <- matrix(data = NA, nrow = total, ncol = length(filterData), byrow = FALSE,dimnames = NULL)
comparison.FL1NormFL2 <- matrix(data = NA, nrow = total, ncol = length(filterData), byrow = FALSE,dimnames = NULL)
#analyzed.samples <- data.frame(matrix(data = NA, nrow = dim(fsApply(flowData, each_col, length))[1], ncol = 5, byrow = TRUE,dimnames = NULL))
analyzed.samples <- data.frame("Well" = character(0), "Strain" = character(0), "Genotype"=character(0), "Ploidy"=character(0), "Media"=character(0) )
#for each sample plot a histogram of the normalized data, raw FSC and raw GFP per row
par(mfrow=c(1,2), mar=c(5.1,2.1,2.1,2.1), oma=c(1.5,2,1,1))

#extract data from flowFrames to plot histograms of values and record summary statistics
for (i in 1:length(filterData)){
 
  temp <- exprs(filterData[[i]]) #exprs() extracts a matrix of the values from the flowframe
 
  sample.info <- sample.sheet[sample.sheet$Well==unlist(strsplit(sampleNames(filterData)[i], "[.]"))[1],] #get the info from the sample sheet corresponding to the well name.
  analyzed.samples <-  rbind(analyzed.samples,sample.info)
  
  ##########################################
  #record summary statistics for the sample#
  ##########################################
  
  #FSC
  summary.stats[i,1] <- median(temp[,1]) 
  summary.stats[i,2] <-mean(temp[,1])  
  summary.stats[i,3] <- sd(temp[,1])
  #FL1
  summary.stats[i,4] <- median(temp[,3])
  summary.stats[i,5] <-mean(temp[,3])  
  summary.stats[i,6] <- sd(temp[,3])
  #FL1 (GFP) divided by FSC
  summary.stats[i,7] <- median(temp[,3]/temp[,1])
  summary.stats[i,8] <-mean(temp[,3]/temp[,1])  
  summary.stats[i,9] <- sd(temp[,3]/temp[,1])
  #FL2
  summary.stats[i,10] <- median(temp[,4])
  summary.stats[i,11] <-mean(temp[,4])  
  summary.stats[i,12] <- sd(temp[,4])
  #FL2 (Red) divided by FSC
  summary.stats[i,13] <- median(temp[,4]/temp[,1])
  summary.stats[i,14] <-mean(temp[,4]/temp[,1])  
  summary.stats[i,15] <- sd(temp[,4]/temp[,1])
  #FL1 (GFP) divided by FL2 (Red)
  summary.stats[i,16] <- median(temp[,3]/temp[,4])
  summary.stats[i,17] <-mean(temp[,3]/temp[,4])  
  summary.stats[i,18] <- sd(temp[,3]/temp[,4])  
  
  ##############################################
  #plot histograms of the channels of interest##
  ##############################################

  ###############
  #Green channel#
  ###############
  
  #FL1 (GFP)
  hist(temp[,3], br=500, xlab = "FL1", main = "FL1") 
  abline(v=gfp.bg, col="yellow", lty=2, lwd=2)
  abline(v=gfp.wt, col="green", lty=2, lwd=2) 
  legend("topleft",  legend=paste("median FL1 = ",round(median(temp[,3]), digits=4),sep=""))

  #GFP divided by FSC
  hist(temp[,3]/temp[,1], br=500, xlim=c(0,1.5), xlab = "FL1/FSC", main = "FL1/FSC") 
  abline(v=gfp.norm, col="green", lty=2, lwd=2 )
  legend("topleft",  legend=paste("median GFP / FSC=",round(median(temp[,3]/temp[,1]), digits=4),sep=""))
  
  mtext(paste("Well = ", sample.info[1,1], " ; Strain = ", sample.info[1,2], " ; Genotype = ", sample.info[1,3], " ; Ploidy = ", sample.info[1,4], " ; Media = ", sample.info[1,5], sep=""), outer = TRUE, cex = 1.0)
  
  ###############
  #Red channel#
  ###############
  #FL2 (Red)
  hist(temp[,4], br=500, xlab = "FL2", main = "FL2", xlim=c(1,8)) 
  abline(v=red.bg, col="yellow", lty=2, lwd=2)
  abline(v=red.wt, col="red", lty=2, lwd=2) 
  legend("topleft",  legend=paste("median FL2=",round(median(temp[,4]), digits=4),sep=""))
 
  #FL2 divided by FSC
  hist(temp[,4]/temp[,1], br=500, xlim=c(0,1.5), xlab = "FL2/FSC", main = "FL2/FSC") 
  abline(v=red.norm, col="red", lty=2, lwd=2 )
  legend("topleft",  legend=paste("median FL2 / FSC=",round(median(temp[,4]/temp[,1]), digits=4),sep=""))

  mtext(paste("Well = ", sample.info[1,1], " ; Strain = ", sample.info[1,2], " ; Genotype = ", sample.info[1,3], " ; Ploidy = ", sample.info[1,4], " ; Media = ", sample.info[1,5], sep=""), outer = TRUE, cex = 1.0)
  
  ###############
  #Other#########
  ###############
  
  #FL1 divided by FL2
  hist(temp[,4]/temp[,3], br=500, xlim=c(0,1.5), xlab = "FL2/FL1", main = "FL1/FL2") 
  abline(v=gfp.red.norm, col="purple", lty=2, lwd=2)
  legend("topleft",  legend=paste("median FL1 / FL2=",round(median(temp[,4]/temp[,3]), digits=4),sep=""))

    #FSC
  hist(temp[,1], br=500, xlab = "FSC", main = "FSC", xlim=c(4,8)) 
  abline(v=haploid.fsc, col="blue", lty=2, lwd=2)
  abline(v=diploid.fsc, col="grey", lty=2, lwd=2)
  legend("topleft",  legend=paste("median FSC=",round(median(temp[,1]), digits=4),sep=""))
  
  mtext(paste("Well = ", sample.info[1,1], " ; Strain = ", sample.info[1,2], " ; Genotype = ", sample.info[1,3], " ; Ploidy = ", sample.info[1,4], " ; Media = ", sample.info[1,5], sep=""), outer = TRUE, cex = 1.0)

print("-------------------------------------------------------")
print("-----------------------------------")
print("----------------------")

  ############################################################
  #keep the data set for generating boxplots comparing values#
  ############################################################
  
  #Note that the amount of data kept for each sample is defined by the lowest count among all the samples.
  comparison.FSC[1:total,i] <- temp[1:total,1] #FSC
  comparison.FL1[1:total,i] <- temp[1:total,3] #FL1 (GFP)
  comparison.FL1NormFsc[1:total,i] <- temp[1:total,3]/temp[1:total,1] #GFP/FSC
  comparison.FL2[1:total,i] <- temp[1:total,4] #FL2 
  comparison.FL2NormFsc[1:total,i] <- temp[1:total,4]/temp[1:total,1] #FL2/FSC
  comparison.FL1NormFL2[1:total,i] <- temp[1:total,3]/temp[1:total,4] #FL1/FL2
  
}

par(mfrow=c(1,1)) #change number of plots per row back to standard
```


###Step 6: Generate boxplot comparing expression values between samples and print table

```{r}
par(mar=c(8.1,4.1,4.1,2.1)) #create more space at lower margin
#boxplot(comparison.FSC, names=sampleNames(filterData), notch = TRUE, col = "gray", ylab="FSC", cex.axis=0.5,las=2, outline=F)
j <- 3 #desired label: 1 = Well, 2 = strain, 3 = genotype, 4 = ploidy, 5 = media

boxplot(comparison.FSC, names=analyzed.samples[,j], notch = TRUE, col = "gray", ylab="FSC", cex.axis=0.5,las=2, outline=F)
abline(h=haploid.fsc, lty=2, col=2)
abline(h=diploid.fsc, lty=2, col=3)

boxplot(comparison.FL1, names=analyzed.samples[,j], notch = TRUE, col = "lightgreen", ylab="FL1", cex.axis=0.5,las=2, outline=F)
abline(h=gfp.bg ,lty=2, lwd=3, col="yellow")
abline(h=gfp.wt, lty = 2, lwd=3, col="green")

boxplot(comparison.FL1NormFsc, names=analyzed.samples[,j], notch = TRUE, col = "green", ylab="FL1/FSC", cex.axis=0.5,las=2, outline=F)
abline(h=gfp.norm, lty=2, lwd=3, col="blue")

boxplot(comparison.FL2, names=analyzed.samples[,j], notch = TRUE, col = "pink", ylab="FL2", cex.axis=0.5,las=2, outline=F)
abline(h=red.bg, lty=2, lwd=3, col="pink")
abline(h=red.wt, lty=2, lwd=3, col="red")

boxplot(comparison.FL2NormFsc, names=analyzed.samples[,j], notch = TRUE, col = "red", ylab="FL2/FSC", cex.axis=0.5,las=2, outline=F)
abline(h=red.norm, lty=2, lwd=3, col="red")

boxplot(comparison.FL1NormFL2, names=analyzed.samples[,j], notch = TRUE, col = "purple", ylab="FL1/FL2", cex.axis=0.5,las=2, outline=F)
abline(h=gfp.red.norm, lty=2, lwd=3, col="purple")

par(mar=c(5.1,4.1,4.1,2.1)) #reset margins to default

#generate a summary table containing all the recorded statistics

summary.stats <- cbind(analyzed.samples, summary.stats)
print(summary.stats)


```

###Step 7: Save plots or tables for use outside of R

```{r}
#export complete data table
write.table(summary.stats, file="Data_Summary.txt", row.names=TRUE, quote=F, sep="\t")

#specify which column of datasheet to include as sample name
j <- 3

#print boxplot of FSC
pdf(file="Boxplot_FSC.pdf", height=8, width=12)
par(mar=c(8.1,4.1,4.1,2.1)) #create more space at lower margin
boxplot(comparison.FSC, names=analyzed.samples[,j], notch = TRUE, col = "gray", ylab="FSC", cex.axis=0.6,las=2, outline=F)
abline(h=haploid.fsc, lty=2, col=2)
abline(h=diploid.fsc, lty=2, col=3)
dev.off()
par(mar=c(5.1,4.1,4.1,2.1)) #reset margins to default

#print boxplot of FL1
pdf(file="Boxplot_FL1.pdf", height=8, width=12)
par(mar=c(8.1,4.1,4.1,2.1)) #create more space at lower margin
boxplot(comparison.FL1, names=analyzed.samples[,j], notch = TRUE, col = "blue", ylab="FL1", cex.axis=0.6,las=2, outline=F)
abline(h=gfp.bg ,lty=2, lwd=3, col="yellow")
abline(h=gfp.wt, lty = 2, lwd=3, col="green")
dev.off()
par(mar=c(5.1,4.1,4.1,2.1)) #reset margins to default

#print boxplot of FL1 normalized by forward scatter
pdf(file="Boxplot_FSCNormalizedGFP.pdf", height=8, width=12)
par(mar=c(8.1,4.1,4.1,2.1)) #create more space at lower margin
boxplot(comparison.FL1NormFsc, names=analyzed.samples[,j], notch = TRUE, col = "green", ylab="GFP normalized by FSC", cex.axis=0.6,las=2, outline=F)
abline(h=gfp.norm, lty=2, lwd=3, col="blue")
dev.off()
par(mar=c(5.1,4.1,4.1,2.1)) #reset margins to default

#print boxplot of FL2
pdf(file="Boxplot_FL2.pdf", height=8, width=12)
par(mar=c(8.1,4.1,4.1,2.1)) #create more space at lower margin
boxplot(comparison.FL2, names=analyzed.samples[,j], notch = TRUE, col = "pink", ylab="FL2", cex.axis=0.6,las=2, outline=F)
abline(h=red.bg, lty=2, lwd=3, col="pink")
abline(h=red.wt, lty=2, lwd=3, col="red")
dev.off()
par(mar=c(5.1,4.1,4.1,2.1)) #reset margins to default

#print boxplot of normalized FL2
pdf(file="Boxplot_FSCnormalizedFL2.pdf", height=8, width=12)
par(mar=c(8.1,4.1,4.1,2.1)) #create more space at lower margin
boxplot(comparison.FL2NormFsc, names=analyzed.samples[,j], notch = TRUE, col = "red", ylab="FL2/FSC", cex.axis=0.6,las=2, outline=F)
abline(h=red.norm, lty=2, lwd=3, col="red")
dev.off()
par(mar=c(5.1,4.1,4.1,2.1)) #reset margins to default

#print boxplot of FL1 normalized by FL2
pdf(file="Boxplot_FL1normalizedFL2.pdf", height=8, width=12)
par(mar=c(8.1,4.1,4.1,2.1)) #create more space at lower margin
boxplot(comparison.FL1NormFL2, names=analyzed.samples[,j], notch = TRUE, col = "purple", ylab="FL1/FL2", cex.axis=0.6,las=2, outline=F)
abline(h=gfp.red.norm, lty=2, lwd=3, col="purple")
dev.off()
par(mar=c(5.1,4.1,4.1,2.1)) #reset margins to default

# # #example of how to to generate a pdf of a histogram
# j <- 2 #change index depending on which sample you want
# 
# temp <- exprs(filterData[[j]]) 
# pdf(file="Example_histogram.pdf", height=6, width=6)
# hist(temp[,3]/temp[,1], br=500, xlim=c(0,1.5), xlab = "Normalized expression signal (GFP/FSC)", main =  sampleNames(filterData)[j]) 
#   legend("topleft",  legend=paste("median=",round(median(temp[,3]/temp[,1]), digits=4),sep=""))
# dev.off()

```






