---
title: "Gresham Lab Flow Core Guide"
author: '`r Sys.info()[7]`'
date: '`r Sys.Date()`'
output:
  html_document:
    fig_caption: yes
    keep_md: yes
    number_sections: yes
    toc: yes
---


**Experiment overview**

Write a detailed description of your experiment here including the goal of the analysis and your interpretation of the results.   
If you still see this text it means that you have not described the experiment and whatever follows is meaningless.
Life is meaningless - but properly documented experiments have context.

###############################

> This code is designed for use with the Accuri flow cytometer, which is equiped with the following lasers and filters

* Blue laser (488 nm)
  + FL1 filter = 514/20nm   GFP
  + FL3 filter = 575/25nm   YFP

* Yellow/green laser (552 nm)
  + FL2 filter = 610/20nm   mCherry, dtomato
  + FL4 filter = 586/15nm   DsRed
  
[You should be familiar with your flow cytometer](https://gencore.bio.nyu.edu/shared-equipment/flow-cytometry/)  

**Requirements**  
In order to run this code you need:  
  + to predefine your gates using the **gating.R** script  
  + the **gates.Rdata** workspace, which contains the gates used in this script  
  + the path of the directory(ies), given the variable names **dir1**, **dir2**... that contain .fcs files named A01.fcs, A02.fcs, A03.fcs...  
  + a tab delimited sample sheet in each directory with the following rows: <Well>	<Strain>	<Genotype>	<Ploidy>	<Media>	<Experiment>  
  + the variable names are changed in chunk 2 named "Variable Names"    




**Output**  
This script generates a summary of results followed by quality control plots.  

#Step 1: Load relevant libraries 

This is a function that just makes sure you have a package, or installs it for you without prompting

```{r Libraries, eval=TRUE}
source("src/requireInstall.R")
requireInstall("flowCore",isBioconductor=T)
requireInstall("flowViz",isBioconductor=T)
#requireInstall("flowStats")
requireInstall("Hmisc")
requireInstall("reshape2")
requireInstall("ggplot2")
#requireInstall("flowWorkspace")
requireInstall("gridExtra")
requireInstall("ggcyto", isBioconductor=T)
```

#Step 2: Read in .fcs files

Read in all data for analysis. Data should be in individual directories that contain .fcs files and a corresponding sample sheet with a generic format. 
FCS file names need to match the `SampleSheet.txt`.

Want to make your `SampleSheet.txt`? Use a GUI spreadsheet thingy,
like excel or googledocs or localc or `edit()` in R.
The format is:

| FileName | Ploidy | Dye | ... |
|:---|:---|:---|:---|
|A01.fcs|1.5ploid|acridineOrange|...|
|A02|2.5ploid|acridineOrange|...|
|A03.fcs|1.5ploid|sytoselect|...|

Where the only mandatory variable name is `FileName`, then all
the others are whatever you're using.

An abitrary number of directories can be used, put the paths in the
`dataDirectoryz` vector. Here we use relative becuase it should be
reproducible between users. You should use ABSOLUTE for your real
work. Don't have this folder? Download it (look up).


```{r readingFCSandSampleSheet, cache=F}
dataDirectoryz <- c("exampleFlowDataset1")

for (dataDirectory in dataDirectoryz) {

  print(paste("Reading",dataDirectory))

  tmpSampleSheet <- read.delim(
    paste0(dataDirectory,"/SampleSheet.txt"),row.names=1)

  tmpFlowSet <- read.flowSet(path=dataDirectory,pattern=".fcs",
    alter.names=TRUE, #why?
    phenoData=new("AnnotatedDataFrame",data=tmpSampleSheet)) 

  if (exists("oneBigFlowSet")) {
    oneBigFlowSet <- rbind2(oneBigFlowSet,tmpFlowSet)
  } else {
    oneBigFlowSet <- tmpFlowSet
  }
}
print("Counted this many events:")
print(fsApply(oneBigFlowSet,nrow))
print("other statz?")
print(fsApply(oneBigFlowSet,each_col,median))
```

Now you have `oneBigFlowSet`. Great. For gating, we'll turn that into
a data.frame:

```{r}
source("src/fc2df.R")
datar <- fc2df(oneBigFlowSet)
```


#Step 3: gate

If you screw it up, delete the RData file of the gates.

```{r gating, cache=F}
gateFilename <- paste0("gatesFor",digest::digest(datar),".RData")
if (file.exists(gateFilename) &&
    readline(paste0("Do you want to load the old gate file (y) ",
      "or define a new one (n)?"))=="y") {
  load(gateFilename)
} else {
  source("src/gator.R")
  gatez <- list()
  gatez[["singlet"]] <- gator2d(datar,ehx="FSC.A",why="FSC.H",
    gateName="singlet") 
  gatez[["cells"]] <- gator2d(datar,ehx="FSC.A",why="SSC.A", 
    gateName="cells") 
  gatez[["gfpPos"]] <- gator2d(datar,ehx="FSC.A",why="FL1.A",
    gateName="gfpPositive") 
  gatez[["gfpNeg"]] <- gator2d(datar,ehx="FSC.A",why="FL1.A", 
    gateName="gfpDepressing") 
  save(file=gateFilename,list=c("gatez"))
}
```

<!--
This also needs an implementation for 1D. I'm thinking that you just
call `gator` function, then you give it a vector of one or two
dimensions you want to gate on. Then you give it a vector of one or
two dimensions to plot. It builds the plot, then the current 
implementation would be if you give it two and two. If you give it
one and one, then it's gating on a histogram with locate(1).
If it's two plot and one gate, then it's a one sided gate on a 2d
scatter. Would be cool.

Would be nice to also have a quadrant gate. Are there functions in
flowCore for this?
-->

how they look?

```{r gateCheck, cache=F}
for (gateName in names(gatez)) {
  print(gateName)
  subdatar <- fc2df(Subset(oneBigFlowSet,gatez[[gateName]]))
  head(subdatar)
}
```
Subset the data by applying sequential gates

```{r doubletGate}
flowData.singlets <- Subset(flowData, pg.singlets) 
fsApply(flowData.singlets, each_col, length)[1:samples.num]
singlets <- fsApply(flowData.singlets, each_col, length)[1:samples.num]
barplot(singlets/total, ylim=c(0,1), ylab = "Proportion singlet cells", las=2, cex.names = 0.5, names.arg=sampleNames(flowData))

#apply debris gate
filteredData <- Subset(flowData.singlets, pg.nondebris) 
fsApply(filteredData, each_col, length)[1:samples.num]
non.debris <- fsApply(filteredData, each_col, length)[1:samples.num]
barplot(non.debris/total, ylim=c(0,1), ylab = "Proportion singlet and nondebris cells", las=2, cex.names = 0.5, names.arg=sampleNames(flowData))

#########
#filteredData is the variable name for the data filtered of doublets and debris that are used for all subsequent analyses
##########

#this gate defines nongfp cells
gfp.neg <- Subset(filteredData, pg.nongfp) 
fsApply(gfp.neg, each_col, length)[1:samples.num]
non.gfp <- fsApply(gfp.neg, each_col, length)[1:samples.num]
barplot(non.gfp/non.debris, ylim=c(0,1), ylab = "Proportion cells with no GFP", las=2, cex.names = 0.5, names.arg=sampleNames(flowData))

#this gate defines gfp cells
gfp.pos <- Subset(filteredData, pg.gfp) 
fsApply(gfp.pos, each_col, length)[1:samples.num]
gfp.cells <- fsApply(gfp.pos, each_col, length)[1:samples.num]
barplot(gfp.cells/non.debris, ylim=c(0,1), ylab = "Proportion cells with GFP", las=2, cex.names = 0.5, names.arg=sampleNames(flowData))

#this gate defines high GFP cells
gfp.hi <- Subset(filteredData, pg.hi.gfp) 
fsApply(gfp.hi, each_col, length)[1:samples.num]
hi.gfp.cells <- fsApply(gfp.hi, each_col, length)[1:samples.num]
barplot(hi.gfp.cells/non.debris, ylim=c(0,1), ylab = "Proportion cells with high GFP", las=2, cex.names = 0.5, names.arg=sampleNames(flowData))
```

#Step 4: Data analysis

##diagnostic values can be defined for plotting purposes
```{r Definition of diagnostic values}
#define critical values that can superimposed on plots for easy visual comparison

gfp.bg <- 3.9  #a background value for GFP
gfp.wt <- 5.9 #a value for wildtype GFP expression
red.bg <- 3.03 #a background value for the red channel
red.wt <- 3.75 #a value for wildtype Red expression
haploid.fsc <- 6e5 #an empirical value for forward scatter for haploids
diploid.fsc <- 7e5 #an empirical value for forward scatter for diploids
gfp.norm <- 0.935 #an empricial value for gfp expression normalized by forward scatter
red.norm <- 0.57 #an empricial value for red expression normalized by forward scatter
gfp.red.norm <- 1.5 #an empricial value for gfp expression normalized by red channel

```

##Extract data from fcs files to generate statistics and boxplots
```{r Data extraction and plotting}
#record summary statistics for each sample in a matrix named summary.stats 
summary.stats <- matrix(data = NA, nrow = length(filteredData), ncol = 18, dimnames = list(sampleNames(filteredData),c("FSC_median","FSC_mean", "FSC_sd","FL1_median", "FL1_mean","FL1_sd","normalizedGFP_median", "normalizedGFP_mean", "normalizedGFP_sd","FL2_median","FL2_mean","FL2_sd","normalizedRed_median","normalizedRed_mean", "normalizedRed_sd","GFPnormalizedByRed_median", "GFPnormalizedByRed_mean","GFPnormalizedByRed_sd")))

#use the sample containing the minimum number of points after filtering for doublets and debris to define the number of data points retained for all samples
sample.size <- min(fsApply(filteredData, each_col, length))  

print(sample.size)

comparison.FSC <- matrix(data = NA, nrow = sample.size, ncol = length(filteredData), byrow = FALSE,dimnames = NULL)
comparison.FL1 <- matrix(data = NA, nrow = sample.size, ncol = length(filteredData), byrow = FALSE,dimnames = NULL)
comparison.FL2 <- matrix(data = NA, nrow = sample.size, ncol = length(filteredData), byrow = FALSE,dimnames = NULL)
comparison.FL1NormFsc <- matrix(data = NA, nrow = sample.size, ncol = length(filteredData), byrow = FALSE,dimnames = NULL)
comparison.FL2NormFsc <- matrix(data = NA, nrow = sample.size, ncol = length(filteredData), byrow = FALSE,dimnames = NULL)
comparison.FL1NormFL2 <- matrix(data = NA, nrow = sample.size, ncol = length(filteredData), byrow = FALSE,dimnames = NULL)

#for each sample plot a histogram of the normalized data, raw FSC and raw GFP per row
par(mfrow=c(1,2), mar=c(5.1,2.1,2.1,2.1), oma=c(1.5,2,1,1))

#extract data from flowFrames to plot histograms of values and record summary statistics
for (i in 1:length(filteredData)){
 
  temp <- exprs(filteredData[[i]]) #exprs() extracts a matrix of the values from the flowframe
 

  ##########################################
  #record summary statistics for the sample#
  ##########################################
  
  #FSC
  summary.stats[i,1] <- median(temp[,1]) 
  summary.stats[i,2] <-mean(temp[,1])  
  summary.stats[i,3] <- sd(temp[,1])
  #FL1
  summary.stats[i,4] <- median(temp[,3])
  summary.stats[i,5] <-mean(temp[,3])  
  summary.stats[i,6] <- sd(temp[,3])
  #FL1 (GFP) divided by FSC
  summary.stats[i,7] <- median(temp[,3]/temp[,1])
  summary.stats[i,8] <-mean(temp[,3]/temp[,1])  
  summary.stats[i,9] <- sd(temp[,3]/temp[,1])
  #FL2
  summary.stats[i,10] <- median(temp[,4])
  summary.stats[i,11] <-mean(temp[,4])  
  summary.stats[i,12] <- sd(temp[,4])
  #FL2 (Red) divided by FSC
  summary.stats[i,13] <- median(temp[,4]/temp[,1])
  summary.stats[i,14] <-mean(temp[,4]/temp[,1])  
  summary.stats[i,15] <- sd(temp[,4]/temp[,1])
  #FL1 (GFP) divided by FL2 (Red)
  summary.stats[i,16] <- median(temp[,3]/temp[,4])
  summary.stats[i,17] <-mean(temp[,3]/temp[,4])  
  summary.stats[i,18] <- sd(temp[,3]/temp[,4])  
  
  ##############################################
  #plot histograms of the channels of interest##
  ##############################################

  ###############
  #Green channel#
  ###############
  
  #FL1 (GFP)
  hist(log10(temp[,3]), br=1000, xlab = "log10(FL1)", main = "FL1") 
  abline(v=gfp.bg, col="yellow", lty=2, lwd=2)
  abline(v=gfp.wt, col="green", lty=2, lwd=2) 
  legend("topleft",  legend=paste("median FL1 = ",round(median(temp[,3]), digits=4),sep=""))

  #GFP divided by FSC
  hist(temp[,3]/temp[,1], br=500, xlab = "FL1/FSC", main = "FL1/FSC") 
  abline(v=gfp.norm, col="green", lty=2, lwd=2 )
  legend("topleft",  legend=paste("median GFP / FSC=",round(median(temp[,3]/temp[,1]), digits=4),sep=""))
  
  mtext(sampleNames(filteredData[i]), outer = TRUE, cex = 1.0)
  
  ###############
  #Red channel#
  ###############
  #FL2 (Red)
  hist(log10(temp[,4]), br=500, xlab = "log10(FL2)", main = "FL2") 
  abline(v=red.bg, col="yellow", lty=2, lwd=2)
  abline(v=red.wt, col="red", lty=2, lwd=2) 
  legend("topleft",  legend=paste("median FL2=",round(median(temp[,4]), digits=4),sep=""))
 
  #FL2 divided by FSC
  hist(temp[,4]/temp[,1], br=500, xlab = "FL2/FSC", main = "FL2/FSC") 
  abline(v=red.norm, col="red", lty=2, lwd=2 )
  legend("topleft",  legend=paste("median FL2 / FSC=",round(median(temp[,4]/temp[,1]), digits=4),sep=""))

  mtext(sampleNames(filteredData[i]), outer = TRUE, cex = 1.0)
  
  ###############
  #Other#########
  ###############
  
  #FL1 divided by FL2
  hist(temp[,4]/temp[,3], br=500, xlab = "FL2/FL1", main = "FL1/FL2") 
  abline(v=gfp.red.norm, col="purple", lty=2, lwd=2)
  legend("topleft",  legend=paste("median FL1 / FL2=",round(median(temp[,4]/temp[,3]), digits=4),sep=""))

    #FSC
  hist(log10(temp[,1]), br=500, xlab = "log10(FSC)", main = "FSC", xlim=c(4,8)) 
  abline(v=haploid.fsc, col="blue", lty=2, lwd=2)
  abline(v=diploid.fsc, col="grey", lty=2, lwd=2)
  legend("topleft",  legend=paste("median FSC=",round(median(temp[,1]), digits=4),sep=""))
  
  mtext(sampleNames(filteredData[i]), outer = TRUE, cex = 1.0)

print("-------------------------------------------------------")
print("-----------------------------------")
print("----------------------")

  ############################################################
  #keep the data set for generating boxplots comparing values#
  ############################################################
  
  #Note that the amount of data kept for each sample is defined by the lowest count among all the samples.
  comparison.FSC[1:sample.size,i] <- temp[1:sample.size,1] #FSC
  comparison.FL1[1:sample.size,i] <- temp[1:sample.size,3] #FL1 (GFP)
  comparison.FL1NormFsc[1:sample.size,i] <- temp[1:sample.size,3]/temp[1:sample.size,1] #GFP/FSC
  comparison.FL2[1:sample.size,i] <- temp[1:sample.size,4] #FL2 
  comparison.FL2NormFsc[1:sample.size,i] <- temp[1:sample.size,4]/temp[1:sample.size,1] #FL2/FSC
  comparison.FL1NormFL2[1:sample.size,i] <- temp[1:sample.size,3]/temp[1:sample.size,4] #FL1/FL2
  
}

par(mfrow=c(1,1)) #change number of plots per row back to standard

```


##Overview of data distributions
```{r Overall data distributions}
par(mar=c(8.1,4.1,4.1,2.1)) #create more space at lower margin

boxplot(comparison.FSC, names=sampleNames(filteredData), notch = TRUE, col = "gray", ylab="FSC", cex.axis=0.5,las=2, outline=F)
abline(h=haploid.fsc, lty=2, col=2)
abline(h=diploid.fsc, lty=2, col=3)

boxplot(comparison.FL1, names=sampleNames(filteredData), notch = TRUE, col = "lightgreen", ylab="FL1", cex.axis=0.5,las=2, outline=F)
abline(h=gfp.bg ,lty=2, lwd=3, col="yellow")
abline(h=gfp.wt, lty = 2, lwd=3, col="green")

boxplot(comparison.FL1NormFsc, names=sampleNames(filteredData), notch = TRUE, col = "green", ylab="FL1/FSC", cex.axis=0.5,las=2, outline=F)
abline(h=gfp.norm, lty=2, lwd=3, col="blue")

boxplot(comparison.FL2, names=sampleNames(filteredData), notch = TRUE, col = "pink", ylab="FL2", cex.axis=0.5,las=2, outline=F)
abline(h=red.bg, lty=2, lwd=3, col="pink")
abline(h=red.wt, lty=2, lwd=3, col="red")

boxplot(comparison.FL2NormFsc, names=sampleNames(filteredData), notch = TRUE, col = "red", ylab="FL2/FSC", cex.axis=0.5,las=2, outline=F)
abline(h=red.norm, lty=2, lwd=3, col="red")

boxplot(comparison.FL1NormFL2, names=sampleNames(filteredData), notch = TRUE, col = "purple", ylab="FL1/FL2", cex.axis=0.5,las=2, outline=F)
abline(h=gfp.red.norm, lty=2, lwd=3, col="purple")

par(mar=c(5.1,4.1,4.1,2.1)) #reset margins to default

#generate a summary table containing all the recorded statistics
print(summary.stats)
summary.stats <- as.data.frame(summary.stats)

```


##Quantitation of relative FL1 signal
```{r}
baseline.FL1 <- summary.stats$FL1_median[1]

barplot(summary.stats$FL1_median/baseline.FL1, ylab="Relative FL1 median expression", las=2, cex.names = 0.5, names.arg=sampleNames(filteredData))

```

##Quantitation of forward scatter
```{r}
baseline.FSC <- summary.stats$FSC_median[1]

barplot(summary.stats$FSC_median/baseline.FSC, ylab="Relative median FSC", las=2, cex.names = 0.5, names.arg=sampleNames(filteredData))

```

##Population composition
```{r}
pop.composition <- rbind(non.gfp/non.debris,gfp.cells/non.debris,hi.gfp.cells/non.debris)
barplot(pop.composition, ylab="Proportion of population", legend=c("No GFP", "Normal GFP", "High GFP"),las=2, cex.names = 0.5,names.arg=sampleNames(filteredData))

```

#Step 5: Quality control

##Gates
```{r}
###First flowset
#Singlets gate
xyplot(FSC.A~FSC.H, data=flowData.1, xlim=c(0,3e6), ylim=c(0,3e6), filter=pg.singlets,  smooth=F, xbin=1024, stat=T, pos=0.5, abs=T, main = "First flowset - singlets gate")

#Debris gate
xyplot(SSC.A ~ FSC.A, data=flowData.1, displayFilter=TRUE, xlim=c(0,3e6), ylim=c(0,3e5), filter=pg.nondebris, smooth=F, xbin=1024, stat=T, pos=0.5, abs=T,  main = "First flowset - nondebris gate")

#Non-fluorescent population gate
xyplot(FL1.A~FSC.A,data=flowData.1, displayFilter=TRUE, xlim=c(0,5e6), ylim=c(0,5e4), filter=pg.nongfp, smooth=F, xbin=1024, stat=T, pos=0.5, abs=T,  main = "First flowset - non GFP gate")

#Fluorescent population gate
xyplot(FL1.A~FSC.A,data=flowData.1, displayFilter=TRUE, xlim=c(0,5e6), ylim=c(0,5e4), filter=pg.gfp, smooth=F, xbin=1024, stat=T, pos=0.5, abs=T, main = "First flowset - GFP gate")

#High fluorescing gate
xyplot(FL1.A~FSC.A,data=flowData.1, xlim=c(0,5e6), ylim=c(0,5e4), filter=pg.hi.gfp, smooth=F, xbin=1024, stat=T, pos=0.5, abs=T,  main = "First flowset - high GFP gate")

################
###Second flowset
#Singlets gate
xyplot(FSC.A~FSC.H, data=flowData.2, xlim=c(0,3e6), ylim=c(0,3e6), filter=pg.singlets,  smooth=F, xbin=1024, stat=T, pos=0.5, abs=T, main = "Second flowset - singlets gate")

#Debris gate
xyplot(SSC.A ~ FSC.A, data=flowData.2, displayFilter=TRUE, xlim=c(0,3e6), ylim=c(0,3e5), filter=pg.nondebris, smooth=F, xbin=1024, stat=T, pos=0.5, abs=T,  main = "Second flowset  - nondebris gate")

#Non-fluorescent population gate
xyplot(FL1.A~FSC.A,data=flowData.2, displayFilter=TRUE, xlim=c(0,5e6), ylim=c(0,5e4), filter=pg.nongfp, smooth=F, xbin=1024, stat=T, pos=0.5, abs=T,  main = "Second flowset - non GFP gate")

#Fluorescent population gate
xyplot(FL1.A~FSC.A,data=flowData.2, displayFilter=TRUE, xlim=c(0,5e6), ylim=c(0,5e4), filter=pg.gfp, smooth=F, xbin=1024, stat=T, pos=0.5, abs=T, main = "Second flowset - GFP gate")

#High fluorescing gate 
xyplot(FL1.A~FSC.A,data=flowData.2, xlim=c(0,5e6), ylim=c(0,5e4), filter=pg.hi.gfp, smooth=F, xbin=1024, stat=T, pos=0.5, abs=T,  main = "Second flowset - high GFP gate")


#####Attempted as loop below to plot each one individually and is not working

for (i in 1:length(filteredData)){

#Singlets gate
xyplot(FSC.A~FSC.H, data=flowData[i], xlim=c(0,3e6), ylim=c(0,3e6), filter=pg.singlets,  smooth=F, xbin=1024, stat=T, pos=0.5, abs=T, main = sampleNames(flowData)[i])

#Debris gate
xyplot(SSC.A ~ FSC.A, data=flowData[i], displayFilter=TRUE, xlim=c(0,3e5), ylim=c(0,3e6), filter=pg.nondebris, smooth=F, xbin=1024, stat=T, pos=0.5, abs=T, main = sampleNames(flowData)[i])

#Non-fluorescent population gate
xyplot(FL1.A~FSC.A,data=flowData[i], displayFilter=TRUE, xlim=c(0,5e6), ylim=c(0,5e4), filter=pg.nongfp, smooth=F, xbin=1024, stat=T, pos=0.5, abs=T, main = sampleNames(flowData)[i])

#Fluorescent population gate
xyplot(FL1.A~FSC.A,data=flowData[i], displayFilter=TRUE, xlim=c(0,5e6), ylim=c(0,5e4), filter=pg.gfp, smooth=F, xbin=1024, stat=T, pos=0.5, abs=T, main = sampleNames(flowData)[i])

#High fluorescing gate
xyplot(FL1.A~FSC.A,data=flowData[i], xlim=c(0,5e6), ylim=c(0,5e4), filter=pg.hi.gfp, smooth=F, xbin=1024, stat=T, pos=0.5, abs=T, main = sampleNames(flowData)[i])

}
```


##Data transformation for visualization
```{r}
#In order to look at QC plots the data is transformed using the logicle transform, which is a log transform for high values that transitions to a linear transformation near zero values 

#This is simply for visualization purposes

lgcl <- logicleTransform(w = 0.5, t= 10000, m=4.5) #the parameters w,t, and m define the transformation parameters

#Dataset 1 tranformation applied to every channel except width and time
dataLGCLTransform <- transform(filteredData,'FSC.A' = lgcl(`FSC.A`), 'SSC.A' =lgcl(`SSC.A`), 'FL1.A' = lgcl(`FL1.A`), 'FL2.A' = lgcl(`FL2.A`), 'FL3.A' = lgcl(`FL3.A`), 'FL4.A' = lgcl(`FL4.A`),'FSC.H' = lgcl(`FSC.H`),'SSC.H' = lgcl(`SSC.H`),'FL1.H' = lgcl(`FL1.H`),'FL2.H' = lgcl(`FL2.H`),'FL3.H' = lgcl(`FL3.H`),'FL4.H' = lgcl(`FL4.H`)) 


```

##Effect of time
```{r}
#The effect of time on signal (of which there shouldn't be any)
i <- 1
xyplot(FL1.A ~ Time, data=dataLGCLTransform[i], smooth=F,  stat=T, pos=0.5, abs=T, xlim=c(150,250), main = sampleNames(filteredData)[i])
i <- 2
xyplot(FL1.A ~ Time, data=dataLGCLTransform[i], smooth=F,  stat=T, pos=0.5, abs=T, xlim=c(150,250), main = sampleNames(filteredData)[i])
i <- 3
xyplot(FL1.A ~ Time, data=dataLGCLTransform[i], smooth=F,  stat=T, pos=0.5, abs=T, xlim=c(150,250), main = sampleNames(filteredData)[i])
####Attempted as loop and will not work 
for (i in 1:length(filteredData)){
xyplot(FL1.A ~ Time, data=dataLGCLTransform[i], smooth=F,  stat=T, pos=0.5, abs=T, xlim=c(150,250), main = sampleNames(filteredData)[i])
}
```

##Plots of FL1 versus FSC
```{r}
i <- 1
xyplot(FL1.A ~ FSC.A, data=dataLGCLTransform[i], smooth=F,  stat=T, pos=0.5, abs=T, xlim=c(4,8), sampleNames(filteredData)[i])
i <- 2
xyplot(FL1.A ~ FSC.A, data=dataLGCLTransform[i], smooth=F,  stat=T, pos=0.5, abs=T, xlim=c(4,8), sampleNames(filteredData)[i])
i <- 3
xyplot(FL1.A ~ FSC.A, data=dataLGCLTransform[i], smooth=F,  stat=T, pos=0.5, abs=T, xlim=c(4,8), sampleNames(filteredData)[i])
####Attempted as loop and will not work 
for (i in 1:length(filteredData)){
xyplot(FL1.A ~ FSC.A, data=dataLGCLTransform[i], smooth=F,  stat=T, pos=0.5, abs=T, xlim=c(4,8), ylim=c(2,6), sampleNames(filteredData)[i])
}
```

##Plots of FSC versus SSC
```{r}
i <- 1
xyplot(SSC.A ~ FSC.A, data=dataLGCLTransform[i], smooth=F,  stat=T, pos=0.5, abs=T, xlim=c(4,8), ylim=c(4,8), sampleNames(filteredData)[i])
i <- 2
xyplot(SSC.A ~ FSC.A, data=dataLGCLTransform[i], smooth=F,  stat=T, pos=0.5, abs=T, xlim=c(4,8), ylim=c(4,8), sampleNames(filteredData)[i])
i <- 3
xyplot(SSC.A ~ FSC.A, data=dataLGCLTransform[i], smooth=F,  stat=T, pos=0.5, abs=T, xlim=c(4,8), ylim=c(4,8), sampleNames(filteredData)[i])
####Attempted as loop and will not work 
for (i in 1:length(filteredData)){
xyplot(SSC.A ~ FSC.A, data=dataLGCLTransform[i], smooth=F,  stat=T, pos=0.5, abs=T, xlim=c(4,8), ylim=c(4,8), sampleNames(filteredData)[i])
}
```





