---
title: "Gresham Lab Flow Core Guide"
author: '`r Sys.info()[7]`'
date: '`r Sys.Date()`'
output:
  html_document:
    fig_caption: yes
    keep_md: yes
    number_sections: yes
    toc: yes
---


**Experiment overview**

Write a detailed description of your experiment here including the goal of the analysis and your interpretation of the results.   
If you still see this text it means that you have not described the experiment and whatever follows is meaningless.
Life is meaningless - but properly documented experiments have context.

For example, this example without context makes me wonder why we're
looking for GFP fluoresence with a dye as the major source of 
variation in the experimental design. Is there a GFP as a 
transcription-and-translation reporter of dye content?

###############################

> This code is designed for use with the Accuri flow cytometer, which is equiped with the following lasers and filters

* Blue laser (488 nm)
  + FL1 filter = 514/20nm   GFP
  + FL3 filter = 575/25nm   YFP

* Yellow/green laser (552 nm)
  + FL2 filter = 610/20nm   mCherry, dtomato
  + FL4 filter = 586/15nm   DsRed
  
[You should be familiar with your flow cytometer](https://gencore.bio.nyu.edu/shared-equipment/flow-cytometry/)  

**Requirements**  
In order to run this code you need:  
  + to predefine your gates using the **gating.R** script  
  + the **gates.Rdata** workspace, which contains the gates used in this script  
  + the path of the directory(ies), given the variable names **dir1**, **dir2**... that contain .fcs files named A01.fcs, A02.fcs, A03.fcs...  
  + a tab delimited sample sheet in each directory with the following rows: <Well>	<Strain>	<Genotype>	<Ploidy>	<Media>	<Experiment>  
  + the variable names are changed in chunk 2 named "Variable Names"    




**Output**  
This script generates a summary of results followed by quality control plots.  

#Step 1: Load relevant libraries 

This is a function that just makes sure you have a package, or installs it for you without prompting

<!--
RStudio seems to have fucked up how they packaged `httpuv`, and 
didn't test a non-gui install, like they should. I'm not alone in 
this problem online,  and `httpuv`
doesn't install like an R package. I'm assuming they slip it into
RStudio, and then build dependencies upon it that won't install
unless you manually install it. So `flowWorkspace` won't load right.

You need to open up another session of R with `--no-init-file` and
`--no-restore` and install the packages.
-->

```{r Libraries, eval=TRUE}
source("src/requireInstall.R")
requireInstall("reshape2")
requireInstall("ggplot2")
requireInstall("flowCore",isBioconductor=T)
requireInstall("flowViz",isBioconductor=T)
requireInstall("Hmisc",isBioconductor=T)
requireInstall("gridExtra")
requireInstall("flowStats",isBioconductor=T)
requireInstall("flowWorkspace",isBioconductor=T)
requireInstall("ggcyto", isBioconductor=T)
```
<!--
In the above chunk, we should specify the end packages and let them
handle dependencies as it sees fit.
-->

#Step 2: Read in .fcs files

Read in all data for analysis. Data should be in individual directories that contain .fcs files and a corresponding sample sheet with a generic format. 
FCS file names need to match the `SampleSheet.txt`.

Want to make your `SampleSheet.txt`? Use a GUI spreadsheet thingy,
like excel or googledocs or localc or `edit()` in R.
The format is:

| FileName | Ploidy | Dye | ... |
|:---|:---|:---|:---|
|A01.fcs|1.5ploid|acridineOrange|...|
|A02|2.5ploid|acridineOrange|...|
|A03.fcs|1.5ploid|sytoselect|...|

Where the only mandatory variable name is `FileName`, then all
the others are whatever you're using.

An abitrary number of directories can be used, put the paths in the
`dataDirectoryz` vector. Here we use relative becuase it should be
reproducible between users. You should use ABSOLUTE for your real
work. Don't have this folder? Download it (look up).


```{r readingFCSandSampleSheet, cache=F}
dataDirectoryz <- c("exampleFlowDataset1")

rm(oneBigFlowSet)
for (dataDirectory in dataDirectoryz) {

  print(paste("Reading",dataDirectory))

  tmpSampleSheet <- read.delim(
    paste0(dataDirectory,"/SampleSheet.txt"),row.names=1)

  tmpFlowSet <- read.flowSet(path=dataDirectory,pattern=".fcs",
    alter.names=TRUE, #why?
    phenoData=new("AnnotatedDataFrame",data=tmpSampleSheet)) 

  sampleNames(tmpFlowSet) <- paste0(dataDirectory,"/",
    sampleNames(tmpFlowSet))
  pData(tmpFlowSet)$name <- sampleNames(tmpFlowSet)

  if (exists("oneBigFlowSet")) {
    oneBigFlowSet <- rbind2(oneBigFlowSet,tmpFlowSet)
  } else {
    oneBigFlowSet <- tmpFlowSet
  }
}
pData(oneBigFlowSet)
print("Counted this many events:")
print(fsApply(oneBigFlowSet,nrow))
print("other statz?")
print(fsApply(oneBigFlowSet,each_col,median))
```

Now you have `oneBigFlowSet`. Great. For gating, we'll turn that into
a data.frame:

```{r}
source("src/fs2df.R")
datar <- fs2df(oneBigFlowSet)
```


#Step 3: gate

If you screw it up, delete the RData file of the gates. Or just
re-run and re-gate it by doing "n".

```{r gating, cache=F}
gateFilename <- paste0("gatesFor",digest::digest(datar),".RData")
if (file.exists(gateFilename) &&
    readline(paste0("Do you want to load the old gate file (y) ",
      "or define a new one (n)?"))=="y") {
  load(gateFilename)
} else {
  source("src/gator.R")
  gatez <- list()
  gatez[["singlet"]] <- gator2d(datar,ehx="FSC.A",why="FSC.H",
    gateName="singlet") 
  gatez[["cells"]] <- gator2d(datar,ehx="FSC.A",why="SSC.A", 
    gateName="cells") 
  gatez[["gfpPos"]] <- gator2d(datar,ehx="FSC.A",why="FL1.A",
    gateName="gfpPositive") 
  gatez[["gfpNeg"]] <- gator2d(datar,ehx="FSC.A",why="FL1.A", 
    gateName="gfpDepressing") 
  save(file=gateFilename,list=c("gatez"))
}
```

<!--
This also needs an implementation for 1D. I'm thinking that you just
call `gator` function, then you give it a vector of one or two
dimensions you want to gate on. Then you give it a vector of one or
two dimensions to plot. It builds the plot, then the current 
implementation would be if you give it two and two. If you give it
one and one, then it's gating on a histogram with locate(1).
If it's two plot and one gate, then it's a one sided gate on a 2d
scatter. Would be cool.

Would be nice to also have a quadrant gate. Are there functions in
flowCore for this?
-->

how they look?

```{r gateCheck, cache=F}
#source("src/gateCheck.R")
#gateCheck()
#make a function so we can re-call it after starting to apply these
for (gateName in names(gatez)) {
  print(gateName)
  ingate  <- data.frame(
    fs2df(Subset(oneBigFlowSet,gatez[[gateName]])),thisGate=T)
  outgate <- data.frame(
    fs2df(Subset(oneBigFlowSet,!gatez[[gateName]])),thisGate=F)
  shuffle <- rbind(ingate,outgate)
  shuffle <- shuffle[sample(1:nrow(shuffle)),]
  names(shuffle)[which(names(shuffle)=="thisGate")] <- gateName
  print(
    ggplot(shuffle)+
      facet_wrap(~name)+
      aes_string(x=colnames(gatez[[gateName]]@boundaries)[1],
                 y=colnames(gatez[[gateName]]@boundaries)[2],
                 col=gateName)+
      geom_point(size=0.2,alpha=0.5)+
      scale_y_log10()+
      scale_x_log10()
  )
}
```
Subset the data by applying sequential gates

```{r gateApply}
rm(filteredDatar)
for (gateName in c("singlet","cells")) {
  print(gateName)
  if (exists("filteredDatar")) {
    filteredDatar  <- Subset(filteredDatar,gatez[[gateName]])
  } else {
    filteredDatar  <- Subset(oneBigFlowSet,gatez[[gateName]])
  }
}
#gateCheck() call would go here
```

Buidling a better datastructure, for later use

```{r unpack}
source("src/splitFSbyGate.R")
gatedFilteredDatar <- filteredDatar
for (gateName in setdiff(names(gatez),c("singlet","cells"))) {
  gatedFilteredDatar <- splitFSbyGate(gatedFilteredDatar,
    gatez[[gateName]])
}
gfdatar <- fs2df(gatedFilteredDatar)
```

#Step 4: Plotz

Into usable form:

```{r summaryPlotz}
head(gfdatar)
mfdatar <- melt(gfdatar,
  id.vars=c("Strain","ul500nMDye","Ploidy","Media","name","gfpPos","gfpNeg"),
  measure.vars=c("FSC.A","FSC.H","FL1.A","FL1.H"))
head(mfdatar)
```

- summary statistics

```{r filteredSummarys}
fsApply(filteredDatar,function(x){
  data.frame(t(each_col(x,summary)))})
fsApply(gatedFilteredDatar,function(x){
  data.frame(t(each_col(x,summary)))})
```

- for each sample plot a histogram of the normalized data, raw FSC and raw GFP per row

```{r histoGramz}
ggplot(mfdatar)+
  facet_grid(name~variable,scales="free")+
  aes(x=log10(value))+
  geom_histogram(bins=50)
```

- extract data from flowFrames to plot histograms of values and record summary statistics

```{r moreSummary}
aggregate(data=mfdatar,value~variable+name,FUN=mean)
aggregate(data=mfdatar,value~variable+name,FUN=median)
```

Specific plotz
```{r}
ggplot(subset(mfdatar,variable%in%c("FL2.A","FL2.H")))+
  aes(x=log10(value))+facet_grid(name~variable)+
  geom_histogram()+
  geom_vline(xintercept=4,col="cyan")

ggplot(subset(gfdatar))+
  aes(x=log10(FL2.A/FSC.A))+
  facet_grid(name~.)+
  geom_histogram()+
  geom_vline(xintercept=0,col="cyan")

ggplot(subset(gfdatar))+
  aes(x=log10(FL1.A/FL2.A))+
  facet_grid(name~.)+
  geom_histogram()+
  geom_vline(xintercept=0,col="cyan")

ggplot(subset(gfdatar))+
  aes(x=log10(FSC.H/FL2.A))+
  facet_grid(name~.)+
  geom_histogram()+
  geom_vline(xintercept=0,col="cyan")

ggplot(subset(mfdatar,variable%in%c("FSC.A","FL1.A","FL2.A")))+
  aes(x=name,y=(value))+facet_grid(~variable,scales="free")+
  geom_violin()+scale_y_log10()+
  theme(axis.text.x=element_text(angle=90))

ggplot(subset(mfdatar,variable%in%c("FSC.A","FL1.A","FL2.A")))+
  aes(x=name,y=(value))+facet_grid(~variable,scales="free")+
  geom_boxplot()+scale_y_log10()+
  theme(axis.text.x=element_text(angle=90))

```

Comparison of FL1.A to 0nM

```{r}
aggregate(data=gfdatar,FL1.A~ul500nMDye,FUN=median)
medianFL1Anodye <- median(subset(gfdatar,ul500nMDye==0)$FL1.A)
ggplot(gfdatar)+
  aes(x=ul500nMDye,y=FL1.A/medianFL1Anodye,group=name)+
  geom_boxplot()+scale_y_log10()+
  theme(axis.text.x=element_text(angle=90))
```

Comparison of FSC.A to 0nM

```{r}
aggregate(data=gfdatar,FSC.A~ul500nMDye,FUN=median)
medianFSCAnodye <- median(subset(gfdatar,ul500nMDye==0)$FSC.A)
ggplot(gfdatar)+
  aes(x=ul500nMDye,y=FSC.A/medianFSCAnodye,group=name)+
  geom_boxplot()+scale_y_log10()+
  theme(axis.text.x=element_text(angle=90))
```

Population composition

```{r}
digits(t(apply(
  data.frame(
    aggregate(data=gfdatar,cbind(gfpPos,gfpNeg)~ul500nMDye,
      FUN=function(x){sum(x==T)}),
    aggregate(data=gfdatar,name~ul500nMDye,FUN=length)
   ),1,function(x){return(c(x[1],x[2:3]/x[5]))}))
```

Step 5: Quality control

> “Great Scientist calculates in terms of the Control of the Quality
>   of the Apparatus, not in terms of earning a living. Agriculture 
>   is inspired by the fear of hunger; study, by an interest in 
>   salary. Great Scientist is concerned about the Apparatus; 
>   not about poverty. Yet.” 
>
>   - Confucious

Scroll up to see how the gates did. Below is an example of `ggplot()`.

```{r}
ggplot(gfdatar)+
  facet_wrap(~ul500nMDye)+
  aes(x=FSC.A,y=FL1.A,col=gfpNeg)+
  geom_point(alpha=0.5,size=0.2)+
  scale_y_log10()+scale_x_log10()
```

Data transformation for visualization

> “Data can make the Transformation great; 
>   it isn’t Transformation which makes the Data great.”
>
>   - Confucious

In order to look at QC plots the data is transformed using the logicle transform, which is a log transform for high values that transitions to a linear transformation near zero values.
This is simply for visualization purposes.

the parameters w,t, and m define the transformation parameters
Below, dataset 1 tranformation applied to every channel except width and time.

```{r}
lgcl <- logicleTransform(w = 0.5, t= 10000, m=4.5)
dataLGCLTransform <- transform(gatedFilteredDatar,'FSC.A' = lgcl(`FSC.A`), 'SSC.A' =lgcl(`SSC.A`), 'FL1.A' = lgcl(`FL1.A`), 'FL2.A' = lgcl(`FL2.A`), 'FL3.A' = lgcl(`FL3.A`), 'FL4.A' = lgcl(`FL4.A`),'FSC.H' = lgcl(`FSC.H`),'SSC.H' = lgcl(`SSC.H`),'FL1.H' = lgcl(`FL1.H`),'FL2.H' = lgcl(`FL2.H`),'FL3.H' = lgcl(`FL3.H`),'FL4.H' = lgcl(`FL4.H`)) 
```

Effect of time



```{r}
#The effect of time on signal (of which there shouldn't be any)
i <- 1
xyplot(FL1.A ~ Time, data=dataLGCLTransform[i], smooth=F,  stat=T, pos=0.5, abs=T, xlim=c(150,250), main = sampleNames(filteredData)[i])
i <- 2
xyplot(FL1.A ~ Time, data=dataLGCLTransform[i], smooth=F,  stat=T, pos=0.5, abs=T, xlim=c(150,250), main = sampleNames(filteredData)[i])
i <- 3
xyplot(FL1.A ~ Time, data=dataLGCLTransform[i], smooth=F,  stat=T, pos=0.5, abs=T, xlim=c(150,250), main = sampleNames(filteredData)[i])
####Attempted as loop and will not work 
for (i in 1:length(filteredData)){
xyplot(FL1.A ~ Time, data=dataLGCLTransform[i], smooth=F,  stat=T, pos=0.5, abs=T, xlim=c(150,250), main = sampleNames(filteredData)[i])
}
```

##Plots of FL1 versus FSC
```{r}
i <- 1
xyplot(FL1.A ~ FSC.A, data=dataLGCLTransform[i], smooth=F,  stat=T, pos=0.5, abs=T, xlim=c(4,8), sampleNames(filteredData)[i])
i <- 2
xyplot(FL1.A ~ FSC.A, data=dataLGCLTransform[i], smooth=F,  stat=T, pos=0.5, abs=T, xlim=c(4,8), sampleNames(filteredData)[i])
i <- 3
xyplot(FL1.A ~ FSC.A, data=dataLGCLTransform[i], smooth=F,  stat=T, pos=0.5, abs=T, xlim=c(4,8), sampleNames(filteredData)[i])
####Attempted as loop and will not work 
for (i in 1:length(filteredData)){
xyplot(FL1.A ~ FSC.A, data=dataLGCLTransform[i], smooth=F,  stat=T, pos=0.5, abs=T, xlim=c(4,8), ylim=c(2,6), sampleNames(filteredData)[i])
}
```

##Plots of FSC versus SSC
```{r}
i <- 1
xyplot(SSC.A ~ FSC.A, data=dataLGCLTransform[i], smooth=F,  stat=T, pos=0.5, abs=T, xlim=c(4,8), ylim=c(4,8), sampleNames(filteredData)[i])
i <- 2
xyplot(SSC.A ~ FSC.A, data=dataLGCLTransform[i], smooth=F,  stat=T, pos=0.5, abs=T, xlim=c(4,8), ylim=c(4,8), sampleNames(filteredData)[i])
i <- 3
xyplot(SSC.A ~ FSC.A, data=dataLGCLTransform[i], smooth=F,  stat=T, pos=0.5, abs=T, xlim=c(4,8), ylim=c(4,8), sampleNames(filteredData)[i])
####Attempted as loop and will not work 
for (i in 1:length(filteredData)){
xyplot(SSC.A ~ FSC.A, data=dataLGCLTransform[i], smooth=F,  stat=T, pos=0.5, abs=T, xlim=c(4,8), ylim=c(4,8), sampleNames(filteredData)[i])
}
```





