---
title: "LTEE_GAP1_CNV_Variant_Analysis"
author: '`r Sys.info()[7]`'
date: '`r Sys.Date()`'
output:
  html_document:
    fig_caption: yes
    keep_md: yes
    number_sections: yes
    toc: yes
---

**Experiment overview**

Write a detailed description of your experiment here including the goal of the analysis and your interpretation of the results.   
If you still see this text it means that you have not described the experiment and whatever follows is meaningless.
###############################

> This code is designed for use with the Accuri flow cytometer, which is equiped with the following lasers and filters

* Blue laser (488 nm)
  + FL1 filter = 514/20nm   GFP
  + FL3 filter = 575/25nm   YFP

* Yellow/green laser (552 nm)
  + FL2 filter = 610/20nm   mCherry, dtomato
  + FL4 filter = 586/15nm   DsRed
  
**Requirements**  

**Output**  


#Step 1: Load relevant libraries 
```{r Libraries, eval=TRUE}
# This is a function that just makes sure you have a package, or installs it for you without prompting

requireInstall <- function(packageName,isBioconductor=F) {
  if ( !try(require(packageName,character.only=T)) ) {
    print(paste0("You don't have ",packageName," accessible, ",
      "I'm gonna install it"))
    if (isBioconductor) {
      source("http://bioconductor.org/biocLite.R")                        
      biocLite(packageName)                                                 
    } else {
      install.packages("packageName", repos = "http://cran.us.r-project.org")
    }
  }
  return(1)
}

#Load libraries
requireInstall("flowCore",isBioconductor=T)
requireInstall("flowViz",isBioconductor=T)
requireInstall("flowStats")
requireInstall("Hmisc")
requireInstall("reshape2")
requireInstall("ggplot2")
requireInstall("flowWorkspace")
requireInstall("ggcyto", isBioconductor=T)
requireInstall("gridExtra")
requireInstall("stringr")
requireInstall("devtools",isBioconductor=T)
requireInstall("ggpubr",isBioconductor=T)
devtools::install_github("guiastrennec/ggplus")
devtools::install_github("kassambara/ggpubr")
library("ggplus")
library("ggpubr")
requireInstall("tidyverse")
filter <- dplyr::filter #Currently required because dplyr is not overriding stats::filter #Seems there are to many filter functions in the libraries used


```

#Step 2: Read in .fcs files, an Rdata file containing the gates sample sheet(s) that contains four columns with 
* column1 = Well
* column2 = Strain
* column3 = Staining
* column4 = Media
* column5 = Userdefined

```{r}
#Set working directory to the folder in which you have stored your .fcs files
#Read in all the fcs files in the directory.

path.data <-"~/Google Drive/MiniStatRun_10_2018/"

#list.folders <- c("LTEE_mCitrine_GAP1_Variants_TON", "LTEE_mCitrine_GAP1_Variants_T00", "LTEE_mCitrine_GAP1_Variants_T06", "LTEE_mCitrine_GAP1_Variants_T07", "LTEE_mCitrine_GAP1_Variants_T08.1", "LTEE_mCitrine_GAP1_Variants_T08.3", "LTEE_mCitrine_GAP1_Variants_T11.1", "LTEE_mCitrine_GAP1_Variants_T11.2", "LTEE_mCitrine_GAP1_Variants_T13.1", "LTEE_mCitrine_GAP1_Variants_T13.2", "LTEE_mCitrine_GAP1_Variants_T14", "LTEE_mCitrine_GAP1_Variants_T15", "LTEE_mCitrine_GAP1_Variants_T18")

list.folders <- c( "LTEE_mCitrine_GAP1_Variants_T00", "LTEE_mCitrine_GAP1_Variants_T06", "LTEE_mCitrine_GAP1_Variants_T07", "LTEE_mCitrine_GAP1_Variants_T08.3", "LTEE_mCitrine_GAP1_Variants_T11.2", "LTEE_mCitrine_GAP1_Variants_T13.1", "LTEE_mCitrine_GAP1_Variants_T14", "LTEE_mCitrine_GAP1_Variants_T15", "LTEE_mCitrine_GAP1_Variants_T18")


#Select folder to load, based on position in list
tp <- 1

#Set To "YES" to load all folders, tp must be set equal to 1
all <- "YES"

flowData <- read.flowSet(path = paste(path.data, list.folders[tp],"/", sep=""), pattern=".fcs", alter.names = TRUE)

sample.sheet <- read.csv(paste(path.data,"Samplesheet_",list.folders[tp],".csv", sep=""))

#Adds a sample sheet data to the pData of the flowset

sampleNames(flowData) <- paste(gsub(" ","_",sample.sheet$Strain),"_T",gsub(" ","_",sample.sheet$Timepoint),"_",sub(" ","_",sample.sheet$Well), sep="")
pData(flowData)$Strain <- gsub(" ","_",sample.sheet$Strain)
pData(flowData)$Genotype <- gsub(" ","_",sample.sheet$Genotype)
pData(flowData)$Population <- gsub(" ","_",sample.sheet$Population)
pData(flowData)$Vessel <- gsub(" ","_",sample.sheet$Vessel)
pData(flowData)$Media <- gsub(" ","_",sample.sheet$Media)
pData(flowData)$Ploidy <- gsub(" ","_",sample.sheet$Ploidy)
pData(flowData)$Well <- gsub(" ","_",sample.sheet$Well)
pData(flowData)$Experiment <- gsub(" ","_",sample.sheet$Experiment)
pData(flowData)$Timepoint <- gsub(" ","_",sample.sheet$Timepoint)
pData(flowData)$Run <- list.folders[1]

if(all == "YES") {
  for(i in 2:length(list.folders)) {
    flowData.temp <- read.flowSet(path = paste(path.data,list.folders[i],"/", sep=""), pattern=".fcs", alter.names = TRUE)

    sample.sheet <- read.csv(paste(path.data,"Samplesheet_",list.folders[i],".csv", sep=""))

    #Adds a sample sheet data to the pData of the flowset
    sampleNames(flowData.temp) <- paste(gsub(" ","_",sample.sheet$Strain),"_T",gsub(" ","_",sample.sheet$Timepoint),"_",sub(" ","_",sample.sheet$Well), sep="")
    pData(flowData.temp)$Strain <- gsub(" ","_",sample.sheet$Strain)
    pData(flowData.temp)$Genotype <- gsub(" ","_",sample.sheet$Genotype)
    pData(flowData.temp)$Population <- gsub(" ","_",sample.sheet$Population)
    pData(flowData.temp)$Vessel <- gsub(" ","_",sample.sheet$Vessel)
    pData(flowData.temp)$Media <- gsub(" ","_",sample.sheet$Media)
    pData(flowData.temp)$Ploidy <- gsub(" ","_",sample.sheet$Ploidy)
    pData(flowData.temp)$Well <- gsub(" ","_",sample.sheet$Well)
    pData(flowData.temp)$Experiment <- gsub(" ","_",sample.sheet$Experiment)
    pData(flowData.temp)$Timepoint <- gsub(" ","_",sample.sheet$Timepoint)
    pData(flowData.temp)$Run <- list.folders[i]

    flowData <- rbind2(flowData, flowData.temp)
  }
}
```

```{r flowSet summaries}
#Check how many cells were counted in each fcs file
total <- fsApply(flowData, each_col, length)[1:length(flowData)] #total counts per sample
print(total)
#Print the medians of data values for each measurement
fsApply(flowData, each_col, median)[1:length(flowData)]

#combine all flowSets into a single flowset
samples.num <- length(flowData)
print(samples.num)
```
#Subsetting the experiments data
```{r Subset the Data}
#sub <- "3"
#subData <- subset(flowData, pData(flowData)$Vessel == sub) #Sperates based on Vessel
#subData <- subset(flowData, pData(flowData)$Timepoint == sub)

subData <- flowData
```

```{r flowSet subsetted data summaries}
#Check how many cells were counted in each fcs file
total <- fsApply(subData, each_col, length)[1:length(subData)] #total counts per sample
print(total)
#Print the medians of data values for each measurement
fsApply(subData, each_col, median)[1:length(subData)]

#combine all flowSets into a single flowset
samples.num <- length(subData)
print(samples.num)
```

#Step 3: apply filters to data and generate plots showing the effect on filtering
#Gating
```{r Application of Gates}
##Subset the data by applying sequential gates##

#Load Gates
load(file = "gates_LTEE_GAP1_Var.RData")

#apply doublet gate to ALL SAMPLES
subData.singlets <- Subset(subData, pg.singlets) 
fsApply(subData.singlets, each_col, length)[1:samples.num]
singlets <- fsApply(subData.singlets, each_col, length)[1:samples.num]
barplot(singlets/total, ylim=c(0,1), ylab = "Proportion singlet cells", las=2, cex.names = 0.5, names.arg=sampleNames(subData))


####GLUTAMINE GATES####
#apply debris gates
filteredData <- Subset(subData.singlets, pg.nondebris) 
fsApply(filteredData, each_col, length)[1:samples.num]
non.debris <- fsApply(filteredData, each_col, length)[1:samples.num]
barplot(non.debris/total, ylim=c(0,1), ylab = "Proportion nondebris cells", las=2, cex.names = 0.5, names.arg=str_sub(sampleNames(filteredData)))

#this gate defines nongfp cells
gfp.neg <- Subset(filteredData, gln.zero) 
fsApply(gfp.neg, each_col, length)[1:samples.num]
non.gfp <- fsApply(gfp.neg, each_col, length)[1:samples.num]
barplot(non.gfp/non.debris, ylim=c(0,1), ylab = "Proportion cells with no GFP", las=2, cex.names = 0.5, names.arg=str_sub(sampleNames(filteredData)))

#this gate defines one copy gfp cells
gfp.one <- Subset(filteredData, gln.one) 
fsApply(gfp.one, each_col, length)[1:samples.num]
gfp.one.cells <- fsApply(gfp.one, each_col, length)[1:samples.num]
barplot(gfp.one.cells/non.debris, ylim=c(0,1), ylab = "Proportion cells with 1 copy GFP", las=2, cex.names = 0.5, names.arg=str_sub(sampleNames(filteredData)))

#this gate defines two copy gfp cells
gfp.two <- Subset(filteredData, gln.two) 
fsApply(gfp.two, each_col, length)[1:samples.num]
gfp.two.cells <- fsApply(gfp.two, each_col, length)[1:samples.num]
  barplot(gfp.two.cells/non.debris, ylim=c(0,1), ylab = "Proportion cells with 2 copy GFP", las=2, cex.names = 0.5, names.arg=str_sub(sampleNames(filteredData)))

#this gate defines thre copy plus gfp cells
gfp.thr <- Subset(filteredData, gln.three) 
fsApply(gfp.thr, each_col, length)[1:samples.num]
gfp.thr.cells <- fsApply(gfp.thr, each_col, length)[1:samples.num]
barplot(gfp.thr.cells/non.debris, ylim=c(0,1), ylab = "Proportion cells with 3 copy+ GFP", las=2, cex.names = 0.5, names.arg=str_sub(sampleNames(filteredData)))
```

#Step 4: Data analysis

##diagnostic values can be defined for plotting purposes
```{r Definition of diagnostic values}
#define critical values that can superimposed on plots for easy visual comparison

gfp.bg <- 3.9  #a background value for GFP
gfp.wt <- 5.9 #a value for wildtype GFP expression
haploid.fsc <- 6e5 #an empirical value for forward scatter for haploids
diploid.fsc <- 7e5 #an empirical value for forward scatter for diploids
gfp.norm <- 0.935 #an empricial value for gfp expression normalized by forward scatter

```

##Extract data from fcs files to generate statistics and boxplots
```{r Data extraction and plotting}
#Transfer data into a dataframe and produce summary stats

#Summary Statistics of Normalized Filtered Data
#Move filtered data into a dataframe
filtered.data <- data.frame(FSC.A=NA,SSC.A=NA,FL1.A=NA, FL2.A=NA, FL3.A=NA, FL4.A=NA, SAMPLE=NA, STRAIN=NA, GENOTYPE=NA, POPULATION=NA, VESSEL=NA, MEDIA=NA, PLOIDY=NA, WELL=NA, EXP=NA, TIMEPOINT=NA, RUN=NA)
stats.data <- data.frame(SAMPLE=NA,STRAIN=NA,POPULATION=NA,VESSEL=NA,TIMEPOINT=NA,COUNT=NA,FSC_MEDIAN=NA,FSC_MEAN=NA,FSC_SD=NA,FL1_MEDIAN=NA,FL1_MEAN=NA,FL1_SD=NA,NORMALIZED_GFP_MEDIAN=NA,NORMALIZED_GFP_MEAN=NA,NORMALIZED_GFP_SD=NA)

for(i in 1:length(filteredData)){
  fsc.a <- exprs(filteredData[[i,1]])
  ssc.a <- exprs(filteredData[[i,2]])
  fl1.a <- exprs(filteredData[[i,3]])
  fl2.a <- exprs(filteredData[[i,4]])
  fl3.a <- exprs(filteredData[[i,5]])
  fl4.a <- exprs(filteredData[[i,6]])
  sample <- sampleNames(filteredData)[i]
  strain <- pData(filteredData)$Strain[i]
  genotype <- pData(filteredData)$Genotype[i]
  population <- pData(filteredData)$Population[i]
  vessel <- pData(filteredData)$Vessel[i]
  media <- pData(filteredData)$Media[i]
  ploidy <- pData(filteredData)$Ploidy[i]
  well <- pData(filteredData)$Well[i]
  exp <- pData(filteredData)$Experiment[i]
  timepoint <- pData(filteredData)$Timepoint[i]
  run <- pData(filteredData)$Run[i]

  filtered.data<-rbind(filtered.data,cbind(FSC.A=fsc.a,SSC.A=ssc.a,FL1.A=fl1.a,FL2.A=fl2.a, FL3.A=fl3.a, FL4.A=fl4.a,SAMPLE=sample, STRAIN=strain, GENOTYPE=genotype, POPULATION = population, VESSEL=vessel, MEDIA=media, PLOIDY=ploidy, WELL=well, EXP=exp, TIMEPOINT=timepoint, RUN=run))
  
  stats.data<-(rbind(stats.data,cbind(SAMPLE=sample,STRAIN=strain,POPULATION=population,VESSEL=vessel,TIMEPOINT=timepoint,COUNT=length(fsc.a),FSC_MEDIAN=median(fsc.a),FSC_MEAN=mean(fsc.a),FSC_SD=sd(fsc.a),FL1_MEDIAN=median(fl1.a),FL1_MEAN=mean(fl1.a),FL1_SD=sd(fl1.a),NORMALIZED_GFP_MEDIAN=median(fl1.a/fsc.a),NORMALIZED_GFP_MEAN=mean(fl1.a/fsc.a),NORMALIZED_GFP_SD=sd(fl1.a/fsc.a))))
}  
  
 #Cleans up DataFrames
  filtered.data<-filtered.data[2:nrow(filtered.data),]
  filtered.data$FSC.A<-as.numeric(filtered.data$FSC.A)
  filtered.data$SSC.A<-as.numeric(filtered.data$SSC.A)
  filtered.data$FL1.A<-as.numeric(filtered.data$FL1.A)
  filtered.data$FL2.A<-as.numeric(filtered.data$FL2.A)
  filtered.data$FL3.A<-as.numeric(filtered.data$FL3.A)
  filtered.data$FL4.A<-as.numeric(filtered.data$FL4.A)
  filtered.data$SAMPLE<-as.factor(filtered.data$SAMPLE)
  filtered.data$STRAIN<-as.factor(filtered.data$STRAIN)
  filtered.data$GENOTYPE<-as.factor(filtered.data$GENOTYPE)
  filtered.data$POPULATION<-as.factor(filtered.data$POPULATION)
  filtered.data$VESSEL<-as.factor(filtered.data$VESSEL)
  filtered.data$MEDIA<-as.factor(filtered.data$MEDIA)
  filtered.data$PLOIDY<-as.factor(filtered.data$PLOIDY)
  filtered.data$WELL<-as.factor(filtered.data$WELL)
  filtered.data$EXP<-as.factor(filtered.data$EXP)
  filtered.data$TIMEPOINT<-as.factor(filtered.data$TIMEPOINT)
  filtered.data$RUN<-as.factor(filtered.data$RUN)
  
  
  stats.data<-stats.data[2:nrow(stats.data),]
  stats.data$SAMPLE<-as.factor(stats.data$SAMPLE)
  stats.data$STRAIN<-as.factor(stats.data$STRAIN)
  stats.data$POPULATION<-as.factor(stats.data$POPULATION)
  stats.data$VESSEL<-as.factor(stats.data$VESSEL)
  stats.data$TIMEPOINT<-as.factor(stats.data$TIMEPOINT)
  stats.data$COUNT<-as.numeric(stats.data$COUNT)
  stats.data$FSC_MEDIAN<-as.numeric(stats.data$FSC_MEDIAN)
  stats.data$FSC_MEAN<-as.numeric(stats.data$FSC_MEAN)    
  stats.data$FSC_SD<-as.numeric(stats.data$FSC_SD)
  stats.data$FL1_MEDIAN<-as.numeric(stats.data$FL1_MEDIAN)
  stats.data$FL1_MEAN<-as.numeric(stats.data$FL1_MEAN)    
  stats.data$FL1_SD<-as.numeric(stats.data$FL1_SD)
  stats.data$NORMALIZED_GFP_MEDIAN<-as.numeric(stats.data$NORMALIZED_GFP_MEDIAN)
  stats.data$NORMALIZED_GFP_MEAN<-as.numeric(stats.data$NORMALIZED_GFP_MEAN)    
  stats.data$NORMALIZED_GFP_SD<-as.numeric(stats.data$NORMALIZED_GFP_SD)
  
```

#Plots

```{r}

#Density Plots
ggplot(filtered.data )+
      geom_density(aes(x = FSC.A), colour = "black")+
  #annotate("text", -Inf, Inf, label = "Top-left", hjust = 0, vjust = 1)+
      annotate("text", x=0.01, y=5, label = paste("FSC MEDIAN-",stats.data$FSC_MEDIAN, sep=" "),colour = "black", size=2)+
      geom_density(aes(x = FL1.A), colour = "green")+
      annotate("text", x=0.01, y=4, label = paste("FL1 MEDIAN-",stats.data$FL1_MEDIAN, sep=" "),colour = "green", size=2)+
      geom_density(aes(x = FL1.A/FSC.A), colour = "blue")+
      annotate("text", x=0.01, y=3,label = paste("FL1/FSC MEDIAN-",signif(stats.data$NORMALIZED_GFP_MEDIAN,4), sep=" "),colour = "blue", size=2)+
      theme()+
      labs(y = "Counts") +
      scale_x_log10()+
      facet_wrap('SAMPLE')

```

##Overview of data distributions
```{r Overall data distributions}
ggplot(filtered.data, aes(SAMPLE,FSC.A)) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 90,vjust=0.5,hjust = 1, size = 6)) +
    stat_boxplot(geom ='errorbar', colour = "grey") +
    geom_boxplot(outlier.shape = NA, colour = "grey") +
    geom_hline(yintercept=haploid.fsc, lty=2, colour = "black") +
    geom_hline(yintercept=diploid.fsc, lty=2, colour = "blue") +
    scale_y_log10()+
    scale_x_discrete(labels=levels(filtered.data$SAMPLE))

ggplot(filtered.data, aes(SAMPLE,FL1.A)) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 90,vjust=0.5,hjust = 1, size = 6)) +
    stat_boxplot(geom ='errorbar', colour = "lightgreen") +
    geom_boxplot(outlier.shape = NA, colour = "lightgreen") +
    geom_hline(yintercept=gfp.bg, lty=2, colour = "yellow") +
    geom_hline(yintercept=gfp.wt, lty=2, colour = "green") +
    labs(title= paste("FL1.A", sep="")) +
    scale_y_log10()+
    scale_x_discrete(labels=levels(filtered.data$SAMPLE))

ggplot(filtered.data, aes(SAMPLE,FL1.A/FSC.A)) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 90,vjust=0.5,hjust = 1, size = 6)) +
    stat_boxplot(geom ='errorbar', colour = "green") +
    geom_boxplot(outlier.shape = NA, colour = "green") +
    geom_hline(yintercept=gfp.norm, lty=2, colour = "blue") +
    scale_y_log10()+
    scale_x_discrete(labels=levels(filtered.data$SAMPLE))

```


```{r Overall data distributions}
par(mar=c(8.1,4.1,4.1,2.1)) #create more space at lower margin

####GLUTAMINE####
boxplot(comparison.FSC, names=str_sub(sampleNames(flowData),1,11), notch = TRUE, col = "gray", ylab="FSC", cex.axis=0.5,las=2, outline=F)
abline(h=haploid.fsc, lty=2, col=2)
abline(h=diploid.fsc, lty=2, col=3)

boxplot(comparison.FL1, names=str_sub(sampleNames(flowData),1,11), notch = TRUE, col = "lightgreen", ylab="FL1", cex.axis=0.5,las=2, outline=F)
abline(h=gfp.bg ,lty=2, lwd=3, col="yellow")
abline(h=gfp.wt, lty = 2, lwd=3, col="green")

boxplot(comparison.FL1NormFsc, names=str_sub(sampleNames(flowData),1,11), notch = TRUE, col = "green", ylab="FL1/FSC", cex.axis=0.5,las=2, outline=F)
abline(h=gfp.norm, lty=2, lwd=3, col="blue")

par(mar=c(5.1,4.1,4.1,2.1)) #reset margins to default

#generate summary tables containing all the recorded statistics
print(summary.stats)
summary.stats <- as.data.frame(summary.stats)


```


##Quantitation of relative FL1 signal

 
```{r Quantitation of relative FL1 signal}

###GLUTAMINE###
baseline.FL1 <- stats.data$FL1_MEDIAN[2] #MUST REPLACE WITH YOUR 1 COPY CONTROL!!
ggplot(stats.data,aes(x=SAMPLE, y = FL1_MEDIAN/baseline.FL1)) +
  geom_col() +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90,vjust=0.5,hjust = 1, size = 6)) +
  scale_x_discrete(labels=stats.data$SAMPLE)+
  ylab("Relative FL1 Median Expression")


```
##Quantitation of forward scatter
```{r Quantitation of forward scatter}
#use 0 copy control
###GLUTAMINE###
baseline.FSC <- stats.data$FSC_MEDIAN[1]
ggplot(stats.data,aes(x=SAMPLE, y = FSC_MEDIAN/baseline.FL1)) +
  geom_col() +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90,vjust=0.5,hjust = 1, size = 6)) +
  scale_x_discrete(labels=stats.data$SAMPLE)+
  ylab("Relative Median FSC")
barplot(summary.stats$FSC_median/baseline.FSC, ylab="Relative median FSC", las=2, cex.names = 0.5, names.arg=str_sub(sampleNames(flowData),1,11))

```
##Population composition

#STILL NEED TO WORK ON UPDATING CODE, MAY NEED TO MODIFY GATING
```{r}
###GLUTAMINE###
#pop.composition <- rbind(non.gfp/non.debris,gfp.one.cells/non.debris,gfp.two.cells/non.debris, gfp.thr.cells/non.debris)


#ggplot(stats.data,aes(x=SAMPLE, y = FL1_MEDIAN/baseline.FL1)) +
#  geom_col() +
#  theme_bw() +
 # theme(axis.text.x = element_text(angle = 90,vjust=0.5,hjust = 1, size = 6)) +
#  scale_x_discrete(labels=stats.data$SAMPLE)+
#  ylab("Proportion of Population")


#barplot(pop.composition, ylab="Proportion of population", legend=c("No GFP", "One copy GFP", "Two copy GFP", "Three+ copy GFP"),las=2, ylim=c(0,1), col=c("black", "grey", "light green", "dark green"), cex.names = 0.5,names.arg=str_sub(sampleNames(flowData),1,11))


```


##Population composition
```{r}
###GLUTAMINE###
pop.composition <- rbind(non.gfp/non.debris,gfp.one.cells/non.debris,gfp.two.cells/non.debris, gfp.thr.cells/non.debris)
barplot(pop.composition, ylab="Proportion of population", legend=c("No GFP", "One copy GFP", "Two copy GFP", "Three+ copy GFP"),las=2, ylim=c(0,1), col=c("black", "grey", "light green", "dark green"), cex.names = 0.5,names.arg=str_sub(sampleNames(flowData),1,11))


```

#Step 5: Quality control

##Gates
```{r Gates}
#Singlets gate
xyplot(FSC.A~FSC.H, data=flowData, xlim=c(0,3e6), ylim=c(0,3e6), filter=pg.singlets,  smooth=F, xbin=1024, stat=T, pos=0.5, abs=T, main = "First flowset - singlets gate")

###Glutamine###
#Debris gate
xyplot(SSC.A ~ FSC.A, data=flowData, displayFilter=TRUE, xlim=c(0,5e6), ylim=c(0,6e5), filter=pg.nondebris, smooth=F, xbin=1024, stat=T, pos=0.5, abs=T,  main = "Glutamine - nondebris gate")

#Non-fluorescent population gate
xyplot(FL1.A~FSC.A,data=filteredData, displayFilter=TRUE, xlim=c(0,5e6), ylim=c(0,6e5), filter=gln.zero, smooth=F, xbin=1024, stat=T, pos=0.5, abs=T,  main = "Glutamine - non GFP gate")

#ONe copy Fluorescent population gate
xyplot(FL1.A~FSC.A,data=filteredData, displayFilter=TRUE, xlim=c(0,5e6), ylim=c(0,6e5), filter=gln.one, smooth=F, xbin=1024, stat=T, pos=0.5, abs=T, main = "Glutamine - One copy GFP gate")

#Two copy fluorescent population gate
xyplot(FL1.A~FSC.A,data=filteredData, displayFilter=TRUE, xlim=c(0,5e6), ylim=c(0,6e5), filter=gln.two, smooth=F, xbin=1024, stat=T, pos=0.5, abs=T, main = "Glutamine - Two copy GFP gate")

#Three copy plus fluorescent population gate
xyplot(FL1.A~FSC.A,data=filteredData, displayFilter=TRUE, xlim=c(0,5e6), ylim=c(0,6e5), filter=gln.three, smooth=F, xbin=1024, stat=T, pos=0.5, abs=T, main = "Glutamine - Three+ copy GFP gate")

```


##Data transformation for visualization
```{r}
#In order to look at QC plots the data is transformed using the logicle transform, which is a log transform for high values that transitions to a linear transformation near zero values 

#This is simply for visualization purposes

lgcl <- logicleTransform(w = 0.5, t= 10000, m=4.5) #the parameters w,t, and m define the transformation parameters

#Tranformation applied to every channel except width and time
dataLGCLTransform <- transform(filteredData,'FSC.A' = lgcl(`FSC.A`), 'SSC.A' =lgcl(`SSC.A`), 'FL1.A' = lgcl(`FL1.A`), 'FL2.A' = lgcl(`FL2.A`), 'FL3.A' = lgcl(`FL3.A`), 'FL4.A' = lgcl(`FL4.A`),'FSC.H' = lgcl(`FSC.H`),'SSC.H' = lgcl(`SSC.H`),'FL1.H' = lgcl(`FL1.H`),'FL2.H' = lgcl(`FL2.H`),'FL3.H' = lgcl(`FL3.H`),'FL4.H' = lgcl(`FL4.H`)) 




```

##Effect of time
```{r}
#The effect of time on signal (of which there shouldn't be any)
i <- 1
xyplot(FL1.A ~ Time, data=dataLGCLTransform[i], smooth=F,  stat=T, pos=0.5, abs=T, xlim=c(150,250), main = sampleNames(filteredData)[i])
i <- 2
xyplot(FL1.A ~ Time, data=dataLGCLTransform[i], smooth=F,  stat=T, pos=0.5, abs=T, xlim=c(150,250), main = sampleNames(filteredData)[i])
i <- 3
xyplot(FL1.A ~ Time, data=dataLGCLTransform[i], smooth=F,  stat=T, pos=0.5, abs=T, xlim=c(150,250), main = sampleNames(filteredData)[i])
```

##Plots of FL1 versus FSC
```{r}
i <- 1
xyplot(FL1.A ~ FSC.A, data=dataLGCLTransform[i], smooth=F,  stat=T, pos=0.5, abs=T, xlim=c(4,8), sampleNames(filteredData)[i])
i <- 2
xyplot(FL1.A ~ FSC.A, data=dataLGCLTransform[i], smooth=F,  stat=T, pos=0.5, abs=T, xlim=c(4,8), sampleNames(filteredData)[i])
i <- 3
xyplot(FL1.A ~ FSC.A, data=dataLGCLTransform[i], smooth=F,  stat=T, pos=0.5, abs=T, xlim=c(4,8), sampleNames(filteredData)[i])
```

##Plots of FSC versus SSC
```{r}
i <- 1
xyplot(SSC.A ~ FSC.A, data=dataLGCLTransform[i], smooth=F,  stat=T, pos=0.5, abs=T, xlim=c(4,8), ylim=c(4,8), sampleNames(filteredData)[i])
i <- 2
xyplot(SSC.A ~ FSC.A, data=dataLGCLTransform[i], smooth=F,  stat=T, pos=0.5, abs=T, xlim=c(4,8), ylim=c(4,8), sampleNames(filteredData)[i])
i <- 3
xyplot(SSC.A ~ FSC.A, data=dataLGCLTransform[i], smooth=F,  stat=T, pos=0.5, abs=T, xlim=c(4,8), ylim=c(4,8), sampleNames(filteredData)[i])
```


##Extract data for further processing
```{r Extract data for further processing}

PopProportion_zeroGFP <- non.gfp/non.debris
PopProportion_oneGFP <- gfp.one.cells/non.debris
PopProportion_twoGFP <- gfp.two.cells/non.debris
PopProportion_threeGFP <- gfp.thr.cells/non.debris
all.data <- cbind(stats.data, PopProportion_zeroGFP, PopProportion_oneGFP, PopProportion_twoGFP, PopProportion_threeGFP, non.debris)
colnames(all.data) <- c(colnames(stats.data), "PopProp_0copy", "PopProp_1copy", "PopProp_2copy", "PopProp_3plus", "Cells counted")


#Save the current dataframe
write.table(all.data, file="DataOut_11302018.csv", row.names=TRUE, quote=F, sep=",")
```



