---
title: "Gresham Lab Floww Cytometry Single Timepoint Analysis"
author: 'G. Avecilla, N. Brandt, S. Lauer, F. Abdul-Rahman, D. Gresham'
date: '`r Sys.Date()`'
output: html_notebook
---

This notebook contains the code necessary to analysis flow cytometry data in the Gresham Lab. 

To analyze flow cytometry data, you MUST use the latest version of this code, available on the [Gresham Lab github](https://github.com/GreshamLab/flow).

**Experimental overview**

Write a detailed description of your experiment here including the goal of the analysis and your interpretation of the results.   
If you still see this text it means that you have not described the experiment and whatever follows is meaningless.

*This code is designed for use with the Accuri flow cytometer, which is equiped with the following lasers and filters*

* Blue laser (488 nm)
* FL1 filter = 514/20nm   GFP
* FL3 filter = 575/25nm   YFP

* Yellow/green laser (552 nm)
* FL2 filter = 610/20nm   mCherry, dtomato
* FL4 filter = 586/15nm   DsRed
  
**Requirements**

In order to run this code you need:

* to predefine your gates using the gating.R script
* the gates.Rdata workspace, which contains the gates to be used in this script
* a tab delimited sample sheet in with the first XXXX columns set up as in the example below
* user defined variables, see below and chunk 1

**Output**  
This script generates quality control plots in the notebook and a file(s) with a summary of results.
The user can generate the output file(s) in three different styles: 

1. As a dataframe converted from fcs with all or some of the data.
2. As a dataframe with summary statistics (e.g. median FL1 per sample)
3. As a new .fcs file with additional information (e.g. phenotype or sample information) appended

**Libraries**

```{r Libraries, eval=TRUE}
# This is a function that just makes sure you have a package, or installs it for you without prompting

requireInstall <- function(packageName,isBioconductor=F) {
  if ( !try(require(packageName,character.only=T)) ) {
    print(paste0("You don't have ",packageName," accessible, ",
      "I'm gonna install it"))
    if (isBioconductor) {
      source("http://bioconductor.org/biocLite.R")                        
      biocLite(packageName)                                                 
    } else {
      install.packages("packageName", repos = "http://cran.us.r-project.org")
    }
  }
  return(1)
}

#Load libraries
requireInstall("openCyto",isBioconductor=T)
requireInstall("tidyverse")
```

  
**Variables and Output Settings**
Variables for the user to set can be found in chunk one. These include both required variables (e.g., working directory), and optional variables (e.g., style of ouput). There are some defaults for these variables.


```{r User Defined Variables}
#working directory
dir = '.'

#file location
path.data = paste(getwd(),"/",sep="")

#fcs run sample name
name = "Test"

#fcs data to extract
extract.FSC_A <- "Yes"
extract.SSC_A <- "Yes"
extract.FL1_A <- "Yes"
extract.FL2_A <- "No"
extract.FL3_A <- "No"
extract.FL4_A <- "No" 
extract.FSC_H <- "No"
extract.SSC_H <- "No"
extract.FL1_H <- "No"
extract.FL2_H <- "No"
extract.FL3_H <- "No"
extract.FL4_H <- "No"
extract.Width <- "No"
extract.Time  <- "No"

#samplesheet parameters
sample.param <- data.frame(SAMPLE=NA, WELL=NA, STRAIN=NA, GENOTYPE=NA, PLOIDY=NA, MEDIA=NA, EXPERIMENT=NA)

#style of output
#FlowSet
save.flowset <- "Yes"
#filename
file.flowset <- "EXPflowdataDATE"
#DataFrame - Individual data points
save.df <- "Yes"
file.df <- "EXPdfDATE"
#DataFrame - Experiment Statistics
save.stats <- "Yes"
file.stats <- "EXPstatsDATE"

```


**Read in Data**
*.fcs files must be in a folder with a unique name and have an accompanying .csv samplesheet
The samplesheet name format must be samplesheet_"unique name".csv
It must contain the following columns, in addition you may add additioanl columns depending on your needs

#This needs to be determined
Need to define names
* column1 = Well
* column2 = Strain
* column3 = Staining
* column4 = Media
* column5 = Userdefined

```{r}


files<-list.files(paste(path.data,name,"/", sep=""),full.names=TRUE)
flowData <- read.ncdfFlowSet(files=files, pattern=".fcs", alter.names = TRUE)


sample.sheet <- read.csv(paste(path.data,"samplesheet_",name,".csv", sep=""))

#Adds a sample sheet data to the pData of the flowset

sampleNames(flowData) <- paste(gsub(" ","_",sample.sheet$Strain),"_",sub(" ","_",sample.sheet$Well), sep="")

#Need to determine samplesheet inputs
pData(flowData)$Well <- sample.sheet$Well
pData(flowData)$Strain <- sample.sheet$Strain
pData(flowData)$Genotype <- sample.sheet$Genotype
pData(flowData)$Ploidy <- sample.sheet$Ploidy
pData(flowData)$Media <- sample.sheet$Media
pData(flowData)$Experiment <- sample.sheet$Experiment


#Load Gates
load(file = "gates.RData")

```

```{r flowSet summaries}
#Check how many cells were counted in each fcs file
total <- fsApply(flowData, each_col, length)[1:length(flowData)] #total counts per sample
print(total)
#Print the medians of data values for each measurement
fsApply(flowData, each_col, median)[1:length(flowData)]

samples.num <- length(flowData)
print(samples.num)
```


** Gating **

Gating will require some more work to make it generic. The serperate gating code will need to be revamped to make it compatiable across different types of experimetns and/or generic enough to be modified depending on experiment
```{r Application of Gates}
##Subset the data by applying sequential gates##

#apply doublet gate to ALL SAMPLES
flowData.singlets <- Subset(flowData, pg.singlets) 
singlets <- fsApply(flowData.singlets, each_col, length)[1:samples.num]
print(singlets)

#apply debris gates
filteredData <- Subset(flowData.singlets, pg.nondebris) 
non.debris <- fsApply(filteredData, each_col, length)[1:samples.num]
print(non.debris)

#this gate defines nonFL1 cells
flone.neg <- Subset(filteredData, pg.nonflone) 
flone.neg.cells <- fsApply(flone.neg, each_col, length)[1:samples.num]
print(flone.neg.cells)

#this gate defines flouresecent cells
flone.pos <- Subset(filteredData, pg.flone) 
flone.pos.cells <- fsApply(flone.pos, each_col, length)[1:samples.num]
print(flone.pos.cells)

```

** Quality control **

##Gates
```{r}

#Singlets gate
xyplot(FSC.A~FSC.H, data=flowData, xlim=c(0,3e6), ylim=c(0,3e6), filter=pg.singlets,  smooth=F, xbin=1024, stat=T, pos=0.5, abs=T, main = "First flowset - singlets gate")

#Debris gate
xyplot(SSC.A ~ FSC.A, data=flowData, displayFilter=TRUE, xlim=c(0,3e6), ylim=c(0,3e5), filter=pg.nondebris, smooth=F, xbin=1024, stat=T, pos=0.5, abs=T,  main = "First flowset - nondebris gate")

#Non-fluorescent population gate
xyplot(FL1.A~FSC.A, data=flowData, displayFilter=TRUE, xlim=c(0,5e6), ylim=c(0,5e4), filter=pg.nonflone, smooth=F, xbin=1024, stat=T, pos=0.5, abs=T,  main = "First flowset - non GFP gate")

#Fluorescent population gate
xyplot(FL1.A~FSC.A, data=flowData, displayFilter=TRUE, xlim=c(0,5e6), ylim=c(0,5e4), filter=pg.flone, smooth=F, xbin=1024, stat=T, pos=0.5, abs=T, main = "First flowset - GFP gate")

#High fluorescing gate
xyplot(FL1.A~FSC.A, data=flowData, xlim=c(0,5e6), ylim=c(0,5e4), filter=pg.hi.flone, smooth=F, xbin=1024, stat=T, pos=0.5, abs=T,  main = "First flowset - high GFP gate")


```

##Data transformation for visualization
```{r}
#In order to look at QC plots the data is transformed using the logicle transform, which is a log transform for high values that transitions to a linear transformation near zero values 

#This is simply for visualization purposes

lgcl <- logicleTransform(w = 0.5, t= 10000, m=4.5) #the parameters w,t, and m define the transformation parameters

#Dataset 1 tranformation applied to every channel except width and time
dataLGCLTransform <- transform(filteredData, 'FSC.A' = lgcl(`FSC.A`), 'SSC.A' =lgcl(`SSC.A`), 'FL1.A' = lgcl(`FL1.A`), 'FL2.A' = lgcl(`FL2.A`), 'FL3.A' = lgcl(`FL3.A`), 'FL4.A' = lgcl(`FL4.A`),'FSC.H' = lgcl(`FSC.H`),'SSC.H' = lgcl(`SSC.H`),'FL1.H' = lgcl(`FL1.H`),'FL2.H' = lgcl(`FL2.H`),'FL3.H' = lgcl(`FL3.H`),'FL4.H' = lgcl(`FL4.H`)) 


```

##Effect of time
```{r}
#The effect of time on signal (of which there shouldn't be any)

xyplot(FL1.A ~ Time, data=dataLGCLTransform, smooth=F,  stat=T, pos=0.5, abs=T, xlim=c(150,250), main = sampleNames(filteredData))
```

##Plots of FL1 versus FSC
```{r}
xyplot(FL1.A ~ FSC.A, data=dataLGCLTransform, smooth=F,  stat=T, pos=0.5, abs=T, xlim=c(4,8), sampleNames(filteredData))
```

##Plots of FSC versus SSC
```{r}
xyplot(SSC.A ~ FSC.A, data=dataLGCLTransform, smooth=F,  stat=T, pos=0.5, abs=T, xlim=c(4,8), ylim=c(4,8), sampleNames(filteredData))
```





```{r Data extraction and plotting}
#Transfer data into a dataframe and produce summary stats

#Summary Statistics of Normalized Filtered Data
#Move filtered data into a dataframe
filtered.data <- sample.param
if(extract.FSC_A == "Yes"){filtered.data<-cbind(filtered.data, FSC.A=NA)}
if(extract.SSC_A == "Yes"){filtered.data<-cbind(filtered.data, SSC.A=NA)}
if(extract.FL1_A == "Yes"){filtered.data<-cbind(filtered.data, FL1.A=NA)}
if(extract.FL2_A == "Yes"){filtered.data<-cbind(filtered.data, FL2.A=NA)}
if(extract.FL3_A == "Yes"){filtered.data<-cbind(filtered.data, FL3.A=NA)}
if(extract.FL4_A == "Yes"){filtered.data<-cbind(filtered.data, FL4.A=NA)}
if(extract.FSC_H == "Yes"){filtered.data<-cbind(filtered.data, FSC.H=NA)}
if(extract.SSC_H == "Yes"){filtered.data<-cbind(filtered.data, SSC.H=NA)}
if(extract.FL1_H == "Yes"){filtered.data<-cbind(filtered.data, FL1.H=NA)}
if(extract.FL2_H == "Yes"){filtered.data<-cbind(filtered.data, FL2.H=NA)}
if(extract.FL3_H == "Yes"){filtered.data<-cbind(filtered.data, FL3.H=NA)}
if(extract.FL4_H == "Yes"){filtered.data<-cbind(filtered.data, FL4.H=NA)}
if(extract.Width == "Yes"){filtered.data<-cbind(filtered.data, Width=NA)}
if(extract.Time == "Yes"){filtered.data<-cbind(filtered.data, Time=NA)}

#stats.data <- data.frame(SAMPLE=NA,STRAIN=NA,POPULATION=NA,VESSEL=NA,TIMEPOINT=NA,COUNT=NA,FSC_MEDIAN=NA,FSC_MEAN=NA,FSC_SD=NA,FL1_MEDIAN=NA,FL1_MEAN=NA,FL1_SD=NA,NORMALIZED_GFP_MEDIAN=NA,NORMALIZED_GFP_MEAN=NA,NORMALIZED_GFP_SD=NA)

for(i in 1:length(filteredData)){
  sample <- sampleNames(filteredData)[i]
  well <- as.character(pData(filteredData)$Well[i])
  strain <- as.character(pData(filteredData)$Strain[i])
  genotype <- as.character(pData(filteredData)$Genotype[i])
  ploidy <- as.character(pData(filteredData)$Ploidy[i])
  media <- as.character(pData(filteredData)$Media[i])
  exp <- as.character(pData(filteredData)$Experiment[i])
  if(extract.FSC_A == "Yes"){fsc.a <- exprs(filteredData[[i,1]])}
  if(extract.SSC_A == "Yes"){ssc.a <- exprs(filteredData[[i,2]])}
  if(extract.FL1_A == "Yes"){fl1.a <- exprs(filteredData[[i,3]])}
  if(extract.FL2_A == "Yes"){fl2.a <- exprs(filteredData[[i,4]])}
  if(extract.FL3_A == "Yes"){fl3.a <- exprs(filteredData[[i,5]])}
  if(extract.FL4_A == "Yes"){fl4.a <- exprs(filteredData[[i,6]])}
  if(extract.FSC_H == "Yes"){fsc.h <- exprs(filteredData[[i,7]])}
  if(extract.SSC_H == "Yes"){ssc.h <- exprs(filteredData[[i,8]])}
  if(extract.FL1_H == "Yes"){fl1.h <- exprs(filteredData[[i,9]])}
  if(extract.FL2_H == "Yes"){fl2.h <- exprs(filteredData[[i,10]])}
  if(extract.FL3_H == "Yes"){fl3.h <- exprs(filteredData[[i,11]])}
  if(extract.FL4_H == "Yes"){fl4.h <- exprs(filteredData[[i,12]])}
  if(extract.Width == "Yes"){width <- exprs(filteredData[[i,11]])}
  if(extract.Time == "Yes"){time <- exprs(filteredData[[i,12]])}

  filtered.data <- rbind(filtered.data, cbind(SAMPLE=sample,WELL=well,STRAIN=strain,GENOTYPE=genotype,PLOIDY=ploidy,MEDIA=media,EXPERIMENT=exp,
                    if(extract.FSC_A == "Yes"){FSC.A=fsc.a},
                    if(extract.SSC_A == "Yes"){SSC.A=ssc.a},
                    if(extract.FL1_A == "Yes"){FL1.A=fl1.a},
                    if(extract.FL2_A == "Yes"){FL2.A=fl2.a},
                    if(extract.FL3_A == "Yes"){FL3.A=fl3.a},
                    if(extract.FL4_A == "Yes"){FL4.A=fl4.a},
                    if(extract.FSC_H == "Yes"){FSC.H=fsc.h},
                    if(extract.SSC_H == "Yes"){SSC.H=ssc.h},
                    if(extract.FL1_H == "Yes"){FL1.H=fl1.h},
                    if(extract.FL2_H == "Yes"){FL2.H=fl2.h},
                    if(extract.FL3_H == "Yes"){FL3.H=fl3.h},
                    if(extract.FL4_H == "Yes"){FL4.H=fl4.h},
                    if(extract.Width == "Yes"){Width=width},
                    if(extract.Time == "Yes"){Time=time}))
  
  
 #stats.data<-(rbind(stats.data,cbind(SAMPLE=sample,STRAIN=strain,POPULATION=population,VESSEL=vessel,TIMEPOINT=timepoint,COUNT=length(fsc.a),FSC_MEDIAN=median(fsc.a),FSC_MEAN=mean(fsc.a),FSC_SD=sd(fsc.a),FL1_MEDIAN=median(fl1.a),FL1_MEAN=mean(fl1.a),FL1_SD=sd(fl1.a),NORMALIZED_GFP_MEDIAN=median(fl1.a/fsc.a),NORMALIZED_GFP_MEAN=mean(fl1.a/fsc.a),NORMALIZED_GFP_SD=sd(fl1.a/fsc.a))))
}  



 #Cleans up DataFrames
  filtered.data<-filtered.data[2:nrow(filtered.data),]
  if(extract.FSC_A == "Yes"){filtered.data$FSC.A<-as.numeric(filtered.data$FSC.A)}
  if(extract.SSC_A == "Yes"){filtered.data$SSC.A<-as.numeric(filtered.data$SSC.A)}
  if(extract.FL1_A == "Yes"){filtered.data$FL1.A<-as.numeric(filtered.data$FL1.A)}
  if(extract.FL2_A == "Yes"){filtered.data$FL2.A<-as.numeric(filtered.data$FL2.A)}
  if(extract.FL3_A == "Yes"){filtered.data$FL3.A<-as.numeric(filtered.data$FL3.A)}
  if(extract.FL4_A == "Yes"){filtered.data$FL4.A<-as.numeric(filtered.data$FL4.A)}
  if(extract.FSC_H == "Yes"){filtered.data$FSC.A<-as.numeric(filtered.data$FSC.A)}
  if(extract.SSC_H == "Yes"){filtered.data$SSC.A<-as.numeric(filtered.data$SSC.A)}
  if(extract.FL1_H == "Yes"){filtered.data$FL1.A<-as.numeric(filtered.data$FL1.A)}
  if(extract.FL2_H == "Yes"){filtered.data$FL2.A<-as.numeric(filtered.data$FL2.A)}
  if(extract.FL3_H == "Yes"){filtered.data$FL3.A<-as.numeric(filtered.data$FL3.A)}
  if(extract.FL4_H == "Yes"){filtered.data$FL4.A<-as.numeric(filtered.data$FL4.A)}
  if(extract.Width == "Yes"){filtered.data$Width<-as.numeric(filtered.data$Width)}
  if(extract.Time == "Yes"){filtered.data$Time<-as.numeric(filtered.data$Time)}
  

  
  
  
  #stats.data<-stats.data[2:nrow(stats.data),]
  #stats.data$SAMPLE<-as.factor(stats.data$SAMPLE)
  #stats.data$STRAIN<-as.factor(stats.data$STRAIN)
  #stats.data$POPULATION<-as.factor(stats.data$POPULATION)
  #stats.data$VESSEL<-as.factor(stats.data$VESSEL)
  #stats.data$TIMEPOINT<-as.factor(stats.data$TIMEPOINT)
  #stats.data$COUNT<-as.numeric(stats.data$COUNT)
  #stats.data$FSC_MEDIAN<-as.numeric(stats.data$FSC_MEDIAN)
 # stats.data$FSC_MEAN<-as.numeric(stats.data$FSC_MEAN)    
  #stats.data$FSC_SD<-as.numeric(stats.data$FSC_SD)
  #stats.data$FL1_MEDIAN<-as.numeric(stats.data$FL1_MEDIAN)
  #stats.data$FL1_MEAN<-as.numeric(stats.data$FL1_MEAN)    
  #stats.data$FL1_SD<-as.numeric(stats.data$FL1_SD)
  #stats.data$NORMALIZED_GFP_MEDIAN<-as.numeric(stats.data$NORMALIZED_GFP_MEDIAN)
  #stats.data$NORMALIZED_GFP_MEAN<-as.numeric(stats.data$NORMALIZED_GFP_MEAN)    
  #stats.data$NORMALIZED_GFP_SD<-as.numeric(stats.data$NORMALIZED_GFP_SD)
```









#Plots
```{r Desnity Plots}
ggplot(filtered.data)+
      geom_density(aes(x = FSC.A), colour = "black")+
      #annotate("text", x=0.01, y=5, label = paste("FSC MEDIAN-",stats.data$FSC_MEDIAN, sep=" "),colour = "black", size=2)+
      theme()+
      labs(y = "Counts", x = "FSC.A") +
      scale_x_log10()+
      facet_wrap('SAMPLE')


ggplot(filtered.data )+
      geom_density(aes(x = FL1.A), colour = "green")+
      #annotate("text", x=0.01, y=4, label = paste("FL1 MEDIAN-",stats.data$FL1_MEDIAN, sep=" "),colour = "green", size=2)+
      theme()+
      labs(y = "Counts", x = "FL1.A") +
      scale_x_log10()+
      facet_wrap('SAMPLE')

ggplot(filtered.data )+
      geom_density(aes(x = FL1.A/FSC.A), colour = "blue")+
      #annotate("text", x=0.01, y=3,label = paste("FL1/FSC MEDIAN-",signif(stats.data$NORMALIZED_GFP_MEDIAN,4), sep=" "),colour = "blue", size=2)+
      theme()+
      labs(y = "Counts",x = "FL1.A/FSC.A") +
      scale_x_log10()+
      facet_wrap('SAMPLE')


```

```{r Data Distribution Plots}
ggplot(filtered.data, aes(SAMPLE,FSC.A)) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 90,vjust=0.5,hjust = 1, size = 6)) +
    stat_boxplot(geom ='errorbar', colour = "grey") +
    geom_boxplot(outlier.shape = NA, colour = "grey") +
    #geom_hline(yintercept=haploid.fsc, lty=2, colour = "black") +
    #geom_hline(yintercept=diploid.fsc, lty=2, colour = "blue") +
    scale_y_log10()+
    scale_x_discrete(labels=levels(filtered.data$SAMPLE))

ggplot(filtered.data, aes(SAMPLE,FL1.A)) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 90,vjust=0.5,hjust = 1, size = 6)) +
    stat_boxplot(geom ='errorbar', colour = "lightgreen") +
    geom_boxplot(outlier.shape = NA, colour = "lightgreen") +
    #geom_hline(yintercept=gfp.bg, lty=2, colour = "yellow") +
    #geom_hline(yintercept=gfp.wt, lty=2, colour = "green") +
    labs(title= paste("FL1.A", sep="")) +
    scale_y_log10()+
    scale_x_discrete(labels=levels(filtered.data$SAMPLE))

ggplot(filtered.data, aes(SAMPLE,FL1.A/FSC.A)) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 90,vjust=0.5,hjust = 1, size = 6)) +
    stat_boxplot(geom ='errorbar', colour = "green") +
    geom_boxplot(outlier.shape = NA, colour = "green") +
    #geom_hline(yintercept=gfp.norm, lty=2, colour = "blue") +
    scale_y_log10()+
    scale_x_discrete(labels=levels(filtered.data$SAMPLE))
```

```{r Quantitation of Signal}

###FL1###
baseline.FL1 <- stats.data$FL1_MEDIAN[2] #MUST REPLACE WITH YOUR FL1 ChannelCONTROL!!
ggplot(stats.data,aes(x=SAMPLE, y = FL1_MEDIAN/baseline.FL1)) +
  geom_col() +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90,vjust=0.5,hjust = 1, size = 6)) +
  scale_x_discrete(labels=stats.data$SAMPLE)+
  ylab("Relative FL1 Median Expression")

###FSC###
baseline.FSC <- stats.data$FSC_MEDIAN[1] #MUST REPLACE WITH YOUR FSC Channel non-flourescense CONTROL!!
ggplot(stats.data,aes(x=SAMPLE, y = FSC_MEDIAN/baseline.FL1)) +
  geom_col() +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90,vjust=0.5,hjust = 1, size = 6)) +
  scale_x_discrete(labels=stats.data$SAMPLE)+
  ylab("Relative Median FSC")
barplot(summary.stats$FSC_median/baseline.FSC, ylab="Relative median FSC", las=2, cex.names = 0.5, names.arg=str_sub(sampleNames(flowData),1,11))

```

#Repupose Barplots into normal plot ourput flow
```{r}
##Subset the data by applying sequential gates##


#apply doublet gate to ALL SAMPLES
flowData.singlets <- Subset(flowData, pg.singlets) 
fsApply(flowData.singlets, each_col, length)[1:samples.num]
singlets <- fsApply(flowData.singlets, each_col, length)[1:samples.num]
barplot(singlets/total, ylim=c(0,1), ylab = "Proportion singlet cells", las=2, cex.names = 0.5, names.arg=sampleNames(flowData))

#apply debris gates
filteredData <- Subset(flowData.singlets, pg.nondebris) 
fsApply(filteredData, each_col, length)[1:samples.num]
non.debris <- fsApply(filteredData, each_col, length)[1:samples.num]
barplot(non.debris/total, ylim=c(0,1), ylab = "Proportion nondebris cells", las=2, cex.names = 0.5, names.arg=str_sub(sampleNames(filteredData)))

#this gate defines nonFL1 cells
flone.neg <- Subset(filteredData, gln.zero) 
fsApply(flone.neg, each_col, length)[1:samples.num]
non.gfp <- fsApply(flone.neg, each_col, length)[1:samples.num]
barplot(flone.neg/non.debris, ylim=c(0,1), ylab = "Proportion cells with no Flourescense", las=2, cex.names = 0.5, names.arg=str_sub(sampleNames(filteredData)))

#this gate defines flouresecent cells
flone.pos <- Subset(filteredData, gln.one) 
fsApply(flone.pos, each_col, length)[1:samples.num]
flone.pos.cells <- fsApply(flone.pos, each_col, length)[1:samples.num]
barplot(flone.pos.cells/non.debris, ylim=c(0,1), ylab = "Proportion cells with Flourescense", las=2, cex.names = 0.5, names.arg=str_sub(sampleNames(filteredData)))

```

##Population composition
```{r}
###GLUTAMINE###
pop.composition <- rbind(non.gfp/non.debris,gfp.one.cells/non.debris,gfp.two.cells/non.debris, gfp.thr.cells/non.debris)
barplot(pop.composition, ylab="Proportion of population", legend=c("No GFP", "One copy GFP", "Two copy GFP", "Three+ copy GFP"),las=2, ylim=c(0,1), col=c("black", "grey", "light green", "dark green"), cex.names = 0.5,names.arg=str_sub(sampleNames(flowData),1,11))


```

##Extract data for further processing
```{r Extract data for further processing}

PopProportion_zeroGFP <- non.gfp/non.debris
PopProportion_oneGFP <- gfp.one.cells/non.debris
PopProportion_twoGFP <- gfp.two.cells/non.debris
PopProportion_threeGFP <- gfp.thr.cells/non.debris
all.data <- cbind(stats.data, PopProportion_zeroGFP, PopProportion_oneGFP, PopProportion_twoGFP, PopProportion_threeGFP, non.debris)
colnames(all.data) <- c(colnames(stats.data), "PopProp_0copy", "PopProp_1copy", "PopProp_2copy", "PopProp_3plus", "Cells counted")


#Save the current dataframe
write.table(all.data, file="DataOut_11302018.csv", row.names=TRUE, quote=F, sep=",")
```

** Saving Data **
```{r Saves Data}
if(save.flowset == "Yes"){save(flowData, paste(file.flowset,".Rdata",sep="")}

if(save.df== "Yes"){}

if(save.stats== "Yes"){}

```


